### 2018-12-14 samplebody-conf.tex
Initial ShareLaTeX Import

\section{Introduction}

\section{The Body of The Paper}

\subsection{Type Changes and {\itshape Special} Characters}

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin\,\ldots{\char'134}end}
construction or with the short form \texttt{\$\,\ldots\$}. You

few examples of in-text equations in context. Notice how
this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX\@; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
are found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table is included in the input file; compare the
placement of the table here with the table in the printed
output of this document.

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more desirable.
Immediately following this sentence is the point at which
Table is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

It is strongly recommended to use the package booktabs
and follow its main principles of typography with respect to tables:
\begin{enumerate}
\item Never, ever use vertical rules.
\item Never use double rules.
\end{enumerate}
It is also a good idea not to overuse horizontal rules.

\subsection{Figures}

As was the case with tables, you may want a figure that spans two
columns.  To do this, and still to ensure proper ``floating''
placement of tables, use the environment \textbf{figure*} to enclose
the figure and its caption.  And don't forget to end the environment
with \textbf{figure*}, not \textbf{figure}!

\subsection{Theorem-like Constructs}

Other common constructs that may occur in your article are the forms
for logical constructs like theorems, axioms, corollaries and proofs.
ACM uses two types of these constructs:  theorem-like and
definition-like.

Here is a theorem:
\begin{theorem}
  Let $f$ be continuous on $[a,b]$.  If $G$ is
  an antiderivative for $f$ on $[a,b]$, then
  \begin{displaymath}
    \int^b_af(t)\,dt = G(b) - G(a).
  \end{displaymath}
\end{theorem}

Here is a definition:
\begin{definition}
  If $z$ is irrational, then by $e^z$ we mean the
  unique number that has
  logarithm $z$:
  \begin{displaymath}
    \log e^z = z.
  \end{displaymath}
\end{definition}

The pre-defined theorem-like constructs are \textbf{theorem},
\textbf{conjecture}, \textbf{proposition}, \textbf{lemma} and
\textbf{corollary}.  The pre-defined de\-fi\-ni\-ti\-on-like constructs are
\textbf{example} and \textbf{definition}.  You can add your own
constructs using the \textsl{amsthm} interface.  The
styles used in the \verb|\theoremstyle| command are \textbf{acmplain}
and \textbf{acmdefinition}.

Another construct is \textbf{proof}, for example,

\begin{proof}
  Suppose on the contrary there exists a real number $L$ such that
  \begin{displaymath}
    \lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
  \end{displaymath}
  Then
  \begin{displaymath}
    l=\lim_{x\rightarrow c} f(x)
    = \lim_{x\rightarrow c}
    \left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
    = \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
    \frac{f(x)}{g(x)} = 0\cdot L = 0,
  \end{displaymath}
  which contradicts our assumption that $l\neq 0$.
\end{proof}

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e., the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{References}
Generated by bibtex from your \texttt{.bib} file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the \texttt{.bbl} file.  Insert that \texttt{.bbl}
file into the \texttt{.tex} source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}

Of course, reading the source code is always useful.  The file
\path{acmart.pdf} contains both the user guide and the commented
code.

\begin{acks}
  The authors would like to thank Dr. Yuhua Li for providing the
  MATLAB code of the \textit{BEPS} method.

  The authors would also like to thank the anonymous referees for
  their valuable comments and helpful suggestions. The work is
  supported by the \grantsponsor{GS501100001809}{National Natural
    Science Foundation of
    China}{http://dx.doi.org/10.13039/501100001809} under Grant
  No.:~\grantnum{GS501100001809}{61273304}
  and~\grantnum[http://www.nnsf.cn/youngscientists]{GS501100001809}{Young
    Scientists' Support Program}.

\end{acks}

### 2018-12-14 PaperTitle.tex
Initial Commit

%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
\documentclass[sigconf]{acmart}
%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

%%%% Proceedings format for SIGPLAN conferences 
% \documentclass[sigplan, anonymous, review]{acmart}

%%%% Proceedings format for SIGCHI conferences
% \documentclass[sigchi, review]{acmart}

%%%% To use the SIGCHI extended abstract template, please visit
% https://www.overleaf.com/read/zzzfqvkmrfzn

\usepackage{booktabs} % For formal tables

% Copyright
% \setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\begin{document}

\title{The Next Release Problem in Real World}
\subtitle{Using Bugzilla dataset.}

\author{Young-kyoung Bae}
\affiliation{%
  \institution{KAIST, 20130298}
}
\email{tardis_95@kaist.ac.kr}

\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings.\footnote{This is an abstract footnote}
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\keywords{ACM proceedings, \LaTeX, text tagging}

\maketitle

\input{PaperBody.tex}

\bibliographystyle{ACM-Reference-Format}
\bibliography{ref}

\end{document}

### 2018-12-14 PaperTitle.tex
The Model is written

@@
 % Copyright
-% \setcopyright{none}
+\setcopyright{none}
 %\setcopyright{acmcopyright}
 %\setcopyright{acmlicensed}
-\setcopyright{rightsretained}
+%\setcopyright{rightsretained}
 %\setcopyright{usgov}
@@
 somewhat loosely, to the formatting guidelines for
-ACM SIG Proceedings.\footnote{This is an abstract footnote}
+ACM SIG Proceedings.
 \end{abstract}
@@
 
-\keywords{ACM proceedings, \LaTeX, text tagging}
+\keywords{NRP, MONRP, Bugzilla}
 

### 2018-12-14 PaperBody.tex
Initial Commit

--- 2018-12-14 samplebody-conf.tex
@@
 
-\section{The Body of The Paper}
+\section{Related Work}
+
+\section{The Model}
+
+Let $R = \{r_1, r_2, \ldots, r_N\}$ is a set of all possible N requirements for software or company and each requirement $r_i \in R$ has its cost and profit, $cost_i \in \mathbb{Z}^+$ and $profit_i \in \mathbb{Z}^+$, to be performed.
+The cost is whatever company have to pay to resolve requirements, for example, money, time and etc.
+The profit is whatever company get by resolving requirements, for example, user satisfaction.
+In this project, we assumed that all requirements are independent.
+It means, there is no prerequisite of requirements.
+The cost vector $Cost$ and the profit vector $Profit$ for requirements are denoted by
+\[
+Cost = \{cost_1, cost_2, \ldots, cost_N\}
+\]
+\[
+Profit = \{profit_1, profit_2, \ldots, profit_N\}
+\]
+
+The company always wants to select requirements for the next release to get the highest sum of profits in the limited budget.
+Let the decision vector $x = \{x_1, x_2, \ldots, x_n\} \in \{0, 1\}$ where $x_i$ is 1 if requirement $i$ is selected and 0 otherwise.
+Then our objective function can be written as below:
+\[
+maximize \sum_{i = 1}^{N} profit_i \cdot x_i
+\]
+subject to
+\[
+\sum_{i = 1}^{N} cost_i \cdot x_i \leq B
+\]
+for some bound $B \in \mathbb{Z}^+$ which represents the limited budget.
 

### 2018-12-14 PaperBody.tex
Related Work added

@@
 \section{Related Work}
+The Next Release Problem(NRP)\cite{NRP} was proposed by Bagnall et al in 2001.
+In this paper, authors considered requirements which can be dependent on other requirements.
+And also, they set the importance(or weight) of each customer who demands for resolving requirements to company.
+
+In the Multi-Objective Next Release Problem(MONRP)\cite{MONRP}, authors tried to solve this problem as the multi-objective optimization problem.
+They applied algorithms(Pareto GA, Single-objective GA, and NSGA-II) and concluded that the NSGA-II is well suited to the MONRP.
+
+After these papers, there are many trials to select the optimal set of requirements.\cite{ILP} \cite{DE} \cite{ACO} However, in almost cases, they used the data set which is randomly generated.
+
+Tonella et al.
+were applied the Interactive Genetic Algorithm and AHP to the NRP and requirements prioritization for real software system as part of the project ACube, but their constraint was number of information about the priority graph, not the limited budget.
 

### 2018-12-15 PaperBody.tex
Simulated Annealing and NSGA2 added (not finished)

@@
 Tonella et al.
-were applied the Interactive Genetic Algorithm and AHP to the NRP and requirements prioritization for real software system as part of the project ACube, but their constraint was number of information about the priority graph, not the limited budget.
+were applied the Interactive Genetic Algorithm and AHP to the NRP and requirements prioritization for real software system as part of the project ACube, but their constraint was number of information about the priority graph, not the limited budget.\cite{IGA}
 
@@
 
-\subsection{Type Changes and {\itshape Special} Characters}
+\section{Algorithms}
+We applied two deterministic algorithms(AHP and ILP) and three heuristic algorithms(SA, GA and NSGA-II) which were introduced as the algorithms well-suited for the NRP in papers.\cite{NRP}\cite{ILP}\cite{IGA}\cite{MONRP}
 
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
+\subsection{Analytic Hierarchy Process}
 
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin\,\ldots{\char'134}end}
-construction or with the short form \texttt{\$\,\ldots\$}. You
+\subsection{Integer Linear Programming}
 
-few examples of in-text equations in context. Notice how
-this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
+\subsection{Simulated Annealing}
+Simulated annealing(SA) is one of the local search techniques which are iterative in nature and rely on the definition of a solution neighbourhood.
+For our NRP project, a requirement-based neighbourhood was defined.
+So the current solution can reach its neighbour by making small changes of decision vector $x$.
 
-\subsubsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
+To apply the SA, we have to define a objective function to get the optimal decision vector:
+\[
+f(\textbf{x}) = \sum_{i = 1}^{N} profit_i \cdot x_i + \lambda \min \Big\{0, \sum_{i = 1}^{N} (cost_i \cdot x_i) - B \Big\}
+\]
 
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX\@; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
+for NRP was introduced in the NRP paper by Bagnall et al.\cite{NRP}
 
-\subsection{Citations}
+In this paper, the cooling schedule by Lundy and Mess\cite{LundySA} is well-suited. Their approach is presented below:
+\[
+    T_{i+1} = \frac{T_i}{1 + \beta T_i}
+\]
+where $T_i$ is the temperature at iteration $i$ and $\beta$ is control parameter. So for the Lundy and Mess cooling schedule, the temperature drops after each move.
+
+In our project, the parameter $\beta$ was set to $1 \times 10^{-8}$ since Bagnall et al. got the best solution for this value in their paper.
+
+\subsection{Genetic Algorithm}
+
+\subsection{NSGA-II}
+
+\begin{algorithm}
+\caption{NSGA-II}\label{alg:nsga2}
+\begin{algorithmic}
+    \While{not stopping condition}
+        \State Let $R_t = P_t \cup Q_t$ ;
+        \State Let $F = $ fast-non-dominated-sort ($R_t$) ; %\Comment{}
+        \State Let $P_{t+1} = \emptyset$ and $i = 1$ ;
+        \While{$|P_{t+1}| + |F_i| \leq N$}
+            \State Apply crowding-distance-assignment($F_i$) ; %\Comment{}
+            \State Let $P_{t+1} = P_{t+1} \cup F_i$ ;
+            \State Let $i = i + 1$
+        \EndWhile
+        \State $Sort(F_i, \prec_n)$
+        \State Let $P_{t+1} = P_{t+1} \cup F_i[1:(N - |P_{t+1}|)]$ ;
+        \State Let $Q_{t+1} = $ make-new-pop($P_{t+1}$) ;
+        \State Let $t = t + 1$ ;
+    \EndWhile\label{euclidendwhile}
+\end{algorithmic}
+\end{algorithm}
+
+\section{Results}
+
+\section{Conclusion}
 

### 2018-12-15 PaperBody.tex
ILP, result, graphs added

--- 2018-12-14 PaperBody.tex
@@
 
+\section{Algorithms}
+\subsection{Analytic Hierarchy Process(AHP)}
+\subsection{Integer Linear Programming(ILP)}
+Integer Linear Programming(ILP) is optimization method whose objective function and constraints are linear, and all variables are integer.
+We referred ILP at the paper \textit{<An Integer Linear Programming approach to the single and bi-objective Next Release Problem>} by N Veerapen et al.
+This paper used ILP solver named \textit{CPLEX}, but it is commercial solver so we used \textit{PuLP}(modeler) and \textit{Gurobi}(solver) for this project.
+\textit{PuLP} is free open source software so users can use it by pip install.
+However general \textit{Gurobi} solver is commercial one so we registered to \textit{Gurobi (www.gurobi.com)} and used \textit{Gurobi} academic version.
+\\
+\subsection{Simulated Annealing(SA)}
+\subsection{Genetic Algorithm(GA)}
+\subsection{NSGA-II}
+
+\begin{table*}
+  \caption{Profit Comparison}
+  \label{tab:commands}
+  \begin{tabular}{cccccl}
+    \toprule
+    &eclipse-log&firefox-log&firefox-priority&firefox-comments+priority\\
+    \midrule
+    Real Cost&50699.70190&262945.49581&262945.49581&262945.49581 \\
+    Real Profit&3489.63592&13025.88085&12210&26332.88085 \\
+    \hline
+    SA&3702.85182&13524.93411&16300.0&28358.2295685 \\
+    GA&3793.5045&13662.38600&16303.0&28522.11861 \\
+    NSGA-II&3822.47741&13700.52067&16518.33333&28729.33476 \\
+    ILP&3825.42768&13768.44722&16336.0&28845.23124 \\
+    AHP&3810.3125825&13758.5577962&16249.0&28811.2749907 \\
+    \bottomrule
+  \end{tabular}
+\end{table*}
+% end the environment with {table*}, NOTE not {table}!
+
+\begin{figure*}[h]
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{bugzilla_eclipse_log(comments)_2016meancost.JPG}
+\caption{bugzilla-eclipse-log(comments)-2016meancost}
+\label{fig:subim1}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{bugzilla_firefox_log(comments)_2016meancost.JPG}
+\caption{bugzilla-firefox-log(comments)-2016meancost}
+\label{fig:subim2}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{bugzilla_firefox_priority_2016meancost.JPG}
+\caption{bugzilla-firefox-priority-2016meancost}
+\label{fig:subim3}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{bugzilla_firefox_comments-priority_2016meancost.JPG}
+\caption{bugzilla-firefox-comments+priority-2016meancost}
+\label{fig:subim4}
+\end{subfigure}
+
+\caption{Profit Comparison for each dataset}
+\label{fig:image1}
+\end{figure*}
+
+\begin{figure*}[h]
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{SA-correlation.JPG}
+\caption{SA}
+\label{fig:subim5}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{GA-correlation.JPG}
+\caption{GA}
+\label{fig:subim6}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{ILP-correlation.JPG}
+\caption{ILP}
+\label{fig:subim7}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{AHP-correlation.JPG}
+\caption{AHP}
+\label{fig:subim8}
+\end{subfigure}
+
+\caption{Cost-Profit Correlation}
+\label{fig:image2}
+\end{figure*}
+
+\begin{figure*}[h]
+\includegraphics[width=0.9\linewidth]{cost-profit-together.JPG}
+\caption{Cost-Profit Correlation in one graph}
+\label{fig:image3}
+\end{figure*}
+
+\section{result}
+At first experiment, we applied five algorithms to four datasets and compared the maximum profit each other.
+In \textbf{table 1}, upper two rows are real cost sum and real profit sum of each datasets.
+Below these rows, there are maximum profits for each algorithms in four datasets.
+At the result, every maximum profits are bigger than real profit sum.
+Also, consumed time to return maximum profit was exceedingly short in ILP and AHP, rather than SA, GA, and NSGA-II.
+\\
+\textbf{Figure 1} is the graphs of \textbf{table 1}.
+Each graph expresses the maximum profit of five algorithms.
+At the result, the maximum profit of ILP is the biggest, and the maximum profit of NSGA-II and AHP is bigger than the maximum profit of SA and GA in most case.
+Except ILP and AHP, maximum profit is high in order of NSGA-II, GA, then SA.
+Peculiar thing is that, in dataset \textit{bugzilla-firefox-priority-2016meancost}, NSGA-II is largely bigger than other four algorithms.
+The reason we suppose is that other three datasets' profit is variety because the number of comments is not bounded, but this dataset's profit is priority, which is varied only in 1, 2, 3, 4, and 5 points.
+In this case, requirements can be seen more similar each other than other datasets.
+This difference could influence the difference of the result.\\
+At experiment 2, we applied four algorithms except NSGA-II to dataset \textit{bugzilla-firefox-comments+priority-2016meancost}.
+At this experiment, we got the maximum profits while changing the cost constraints.
+The result is expressed in \textbf{Figure 2} and \textbf{Figure 3}.
+\textbf{Figure 2} expresses maximum profits on each cost, and \textbf{Figure 3} is integrating graph of \textbf{Figure 2} because of comparing the difference for four algorithms.
+\\
+The result is that they are all increasing almost linearly and similarly.
+One of the reasons to perform this experiment was that we wondered if there is a peculiar part in cost-profit graph.(if there is exceeding increase in profit) And at the result, there is no prominently peculiar part, and all the results are increasing normally.
 \subsection{Type Changes and {\itshape Special} Characters}
@@
 in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
 

### 2018-12-15 PaperBody.tex

--- 2018-12-15 PaperBody.tex
@@
 \subsection{Integer Linear Programming}
+Integer Linear Programming(ILP) is optimization method whose objective function and constraints are linear, and all variables are integer.
+Reference paper used ILP solver named \textit{CPLEX}, but it is commercial solver so we used \textit{PuLP}(modeler) and \textit{Gurobi}(solver) for this project.
+\textit{PuLP} is free open source software so users can use it by pip install.
+However general \textit{Gurobi} solver is commercial one so we registered to \textit{Gurobi (www.gurobi.com)} and used \textit{Gurobi} academic version.
 
@@
 
-\section{Results}
-
-\section{Conclusion}
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-are found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table is included in the input file; compare the
-placement of the table here with the table in the printed
-output of this document.
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
 \begin{table*}
-  \caption{Some Typical Commands}
+  \caption{Profit Comparison}
   \label{tab:commands}
-  \begin{tabular}{ccl}
+  \begin{tabular}{cccccl}
     \toprule
-    Command &A Number & Comments\\
+    &eclipse-log&firefox-log&firefox-priority&firefox-comments+priority\\
     \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
+    Real Cost&50699.70190&262945.49581&262945.49581&262945.49581 \\
+    Real Profit&3489.63592&13025.88085&12210&26332.88085 \\
+    \hline
+    SA&3702.85182&13524.93411&16300.0&28358.2295685 \\
+    GA&3793.5045&13662.38600&16303.0&28522.11861 \\
+    NSGA-II&3822.47741&13700.52067&16518.33333&28729.33476 \\
+    ILP&3825.42768&13768.44722&16336.0&28845.23124 \\
+    AHP&3810.3125825&13758.5577962&16249.0&28811.2749907 \\
     \bottomrule
@@
 
-It is strongly recommended to use the package booktabs
-and follow its main principles of typography with respect to tables:
-\begin{enumerate}
-\item Never, ever use vertical rules.
-\item Never use double rules.
-\end{enumerate}
-It is also a good idea not to overuse horizontal rules.
+\begin{figure*}[h]
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{bugzilla_eclipse_log(comments)_2016meancost.JPG}
+\caption{bugzilla-eclipse-log(comments)-2016meancost}
+\label{fig:subim1}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{bugzilla_firefox_log(comments)_2016meancost.JPG}
+\caption{bugzilla-firefox-log(comments)-2016meancost}
+\label{fig:subim2}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{bugzilla_firefox_priority_2016meancost.JPG}
+\caption{bugzilla-firefox-priority-2016meancost}
+\label{fig:subim3}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{bugzilla_firefox_comments-priority_2016meancost.JPG}
+\caption{bugzilla-firefox-comments+priority-2016meancost}
+\label{fig:subim4}
+\end{subfigure}
 
-\subsection{Figures}
+\caption{Profit Comparison for each dataset}
+\label{fig:image1}
+\end{figure*}
 
-As was the case with tables, you may want a figure that spans two
-columns.  To do this, and still to ensure proper ``floating''
-placement of tables, use the environment \textbf{figure*} to enclose
-the figure and its caption.  And don't forget to end the environment
-with \textbf{figure*}, not \textbf{figure}!
+\begin{figure*}[h]
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{SA-correlation.JPG}
+\caption{SA}
+\label{fig:subim5}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{GA-correlation.JPG}
+\caption{GA}
+\label{fig:subim6}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{ILP-correlation.JPG}
+\caption{ILP}
+\label{fig:subim7}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\linewidth]{AHP-correlation.JPG}
+\caption{AHP}
+\label{fig:subim8}
+\end{subfigure}
 
-\subsection{Theorem-like Constructs}
+\caption{Cost-Profit Correlation}
+\label{fig:image2}
+\end{figure*}
 
-Other common constructs that may occur in your article are the forms
-for logical constructs like theorems, axioms, corollaries and proofs.
-ACM uses two types of these constructs:  theorem-like and
-definition-like.
+\begin{figure*}[h]
+\includegraphics[width=0.9\linewidth]{cost-profit-together.JPG}
+\caption{Cost-Profit Correlation in one graph}
+\label{fig:image3}
+\end{figure*}
 
-Here is a theorem:
-\begin{theorem}
-  Let $f$ be continuous on $[a,b]$.  If $G$ is
-  an antiderivative for $f$ on $[a,b]$, then
-  \begin{displaymath}
-    \int^b_af(t)\,dt = G(b) - G(a).
-  \end{displaymath}
-\end{theorem}
-
-Here is a definition:
-\begin{definition}
-  If $z$ is irrational, then by $e^z$ we mean the
-  unique number that has
-  logarithm $z$:
-  \begin{displaymath}
-    \log e^z = z.
-  \end{displaymath}
-\end{definition}
-
-The pre-defined theorem-like constructs are \textbf{theorem},
-\textbf{conjecture}, \textbf{proposition}, \textbf{lemma} and
-\textbf{corollary}.  The pre-defined de\-fi\-ni\-ti\-on-like constructs are
-\textbf{example} and \textbf{definition}.  You can add your own
-constructs using the \textsl{amsthm} interface.  The
-styles used in the \verb|\theoremstyle| command are \textbf{acmplain}
-and \textbf{acmdefinition}.
-
-Another construct is \textbf{proof}, for example,
-
-\begin{proof}
-  Suppose on the contrary there exists a real number $L$ such that
-  \begin{displaymath}
-    \lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-  \end{displaymath}
-  Then
-  \begin{displaymath}
-    l=\lim_{x\rightarrow c} f(x)
-    = \lim_{x\rightarrow c}
-    \left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-    = \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-    \frac{f(x)}{g(x)} = 0\cdot L = 0,
-  \end{displaymath}
-  which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-\section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e., the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{References}
-Generated by bibtex from your \texttt{.bib} file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the \texttt{.bbl} file.  Insert that \texttt{.bbl}
-file into the \texttt{.tex} source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-
-Of course, reading the source code is always useful.  The file
-\path{acmart.pdf} contains both the user guide and the commented
-code.
-
-\begin{acks}
-  The authors would like to thank Dr. Yuhua Li for providing the
-  MATLAB code of the \textit{BEPS} method.
-
-  The authors would also like to thank the anonymous referees for
-  their valuable comments and helpful suggestions. The work is
-  supported by the \grantsponsor{GS501100001809}{National Natural
-    Science Foundation of
-    China}{http://dx.doi.org/10.13039/501100001809} under Grant
-  No.:~\grantnum{GS501100001809}{61273304}
-  and~\grantnum[http://www.nnsf.cn/youngscientists]{GS501100001809}{Young
-    Scientists' Support Program}.
-
-\end{acks}
+\section{Results}
+At first experiment, we applied five algorithms to four datasets and compared the maximum profit each other.
+In \textbf{table 1}, upper two rows are real cost sum and real profit sum of each datasets.
+Below these rows, there are maximum profits for each algorithms in four datasets.
+At the result, every maximum profits are bigger than real profit sum.
+Also, consumed time to return maximum profit was exceedingly short in ILP and AHP, rather than SA, GA, and NSGA-II.
+\\
+\textbf{Figure 1} is the graphs of \textbf{table 1}.
+Each graph expresses the maximum profit of five algorithms.
+At the result, the maximum profit of ILP is the biggest, and the maximum profit of NSGA-II and AHP is bigger than the maximum profit of SA and GA in most case.
+Except ILP and AHP, maximum profit is high in order of NSGA-II, GA, then SA.
+Peculiar thing is that, in dataset \textit{bugzilla-firefox-priority-2016meancost}, NSGA-II is largely bigger than other four algorithms.
+The reason we suppose is that other three datasets' profit is variety because the number of comments is not bounded, but this dataset's profit is priority, which is varied only in 1, 2, 3, 4, and 5 points.
+In this case, requirements can be seen more similar each other than other datasets.
+This difference could influence the difference of the result.\\
+At experiment 2, we applied four algorithms except NSGA-II to dataset \textit{bugzilla-firefox-comments+priority-2016meancost}.
+At this experiment, we got the maximum profits while changing the cost constraints.
+The result is expressed in \textbf{Figure 2} and \textbf{Figure 3}.
+\textbf{Figure 2} expresses maximum profits on each cost, and \textbf{Figure 3} is integrating graph of \textbf{Figure 2} because of comparing the difference for four algorithms.
+\\
+The result is that they are all increasing almost linearly and similarly.
+One of the reasons to perform this experiment was that we wondered if there is a peculiar part in cost-profit graph.(if there is exceeding increase in profit) And at the result, there is no prominently peculiar part, and all the results are increasing normally.
+\section{Conclusion}

### 2018-12-16 PaperBody.tex
SA edited

@@
 \subsection{Integer Linear Programming}
-Integer Linear Programming(ILP) is optimization method whose objective function and constraints are linear, and all variables are integer.
-Reference paper used ILP solver named \textit{CPLEX}, but it is commercial solver so we used \textit{PuLP}(modeler) and \textit{Gurobi}(solver) for this project.
-\textit{PuLP} is free open source software so users can use it by pip install.
-However general \textit{Gurobi} solver is commercial one so we registered to \textit{Gurobi (www.gurobi.com)} and used \textit{Gurobi} academic version.
+The Integer Linear Programming(ILP) is optimization method whose objective function and constraints are linear, and all variables are integer.
+The NRP can be treated as the ILP since each element of the decision vector $\textbf{x}$ is 0 or 1 and our constraint, the limited budget, is also linear.
+So we applied the ILP solver to the NRP problem.
+
+Reference paper\cite{ILP} used ILP solver named \textit{CPLEX}, but it is commercial solver so we used \textit{PuLP}(modeler) and \textit{Gurobi}(solver) for this project.
+\textit{PuLP} is free open source software so users can use it.
+However, general \textit{Gurobi} solver is commercial one so we registered to \textit{Gurobi (www.gurobi.com)} and used \textit{Gurobi} academic version.
 
@@
 \]
+where $\textbf{x}$ is the decision vector, $f$ is our objective function and $\lambda$ is control parameter.
+We can impose a penalty if the sum of costs exceed the limited budget by using the control parameter $\lambda$.
+This objective function is also used in genetic algorithm to evaluate each chromosome.
 
-for NRP was introduced in the NRP paper by Bagnall et al.\cite{NRP}
-
-In this paper, the cooling schedule by Lundy and Mess\cite{LundySA} is well-suited. Their approach is presented below:
+In the NRP paper\cite{NRP}, the cooling schedule by Lundy and Mess\cite{LundySA} is well-suited. Their approach is presented below:
 \[
@@
 
-In our project, the parameter $\beta$ was set to $1 \times 10^{-8}$ since Bagnall et al. got the best solution for this value in their paper.
+In our project, the parameter $\lambda$ and $\beta$ were set to 5 and $1 \times 10^{-8}$ since Bagnall et al. got the best solution for this value in their paper.
 

### 2018-12-16 PaperTitle.tex
Simulated Annealing and NSGA2 added (not finished)
ILP, result, graphs added
adding github account to author
Updates from ShareLaTeX

@@
 \usepackage{booktabs} % For formal tables
+\usepackage{graphicx}
+\usepackage{subcaption}
+
+\usepackage[english]{babel}
+\usepackage[utf8]{inputenc}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 
@@
 %\setcopyright{cagovmixed}
+
+\graphicspath{{images/}}
 
@@
 
+\author{Jin-woo Lee}
+\affiliation{%
+    \institution{KAIST, 20120774}
+}
+\email{hiall21@kaist.ac.kr}
+
+\author{Sue-hwan Lee}
+\affiliation{%
+    \institution{KAIST, 20110686}
+}
+\email{wwa098@kaist.ac.kr}
+
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms,
-somewhat loosely, to the formatting guidelines for
-ACM SIG Proceedings.
+This report provides the work of applying NRP problems to real-world problem.
+The NRP problem is where the company chooses which requirements to reflect when releasing the next version.
+We criticize the fact that most of the previous papers extracted results using random variables rather than actual data values.
+To improve that, we've taken the data out of the Bugzilla in Firefox and Eclipse repositories, and we've solved the problem of choosing which bugs need to be fixed in the next version.
+We compared performance by applying several known algorithms, SA, GA NSGA2, IHP, and AHP.
+This report shows how well the application of search-based algorithms to NRP problems in the real world, and which algorithms are the most effective.
 \end{abstract}
@@
 
-\keywords{NRP, MONRP, Bugzilla}
+\keywords{NRP, MONRP, Bugzilla, Firefox, Eclipse}
 

### 2018-12-16 PaperBody.tex

@@
 \section{Introduction}
+ The NRP problem is the choice of what requirements the company will reflect when making the next version of the product.
+This problem is primarily aimed at helping the company get the most profit from limited costs.
+However, most of the previous studies were using random variables, not actual data values.
+
+ The reason is that first of all, it's quite difficult to define the cost and the profit.
+Cost and profits are quite difficult to quantify.
+Both have to be calculated before the actual requirements are applied, so we have to use estimates value, rather than actual values.
+The second reason is that the requirements for the company's next production are highly secured data to the company and are very difficult to use in real research.
+Even if your company provides data, the actual results are prohibited to open, and this often results in post-processing after the release.
+
+ We point out that these processes are wrong.
+The real NRP problem is that the cost and profit are not independent, and because it is used in the real industry, the process of obtaining the cost and profit has to be included to entire process.
+Also, importing and writing data from the future makes it difficult for research results to be applied to actual industrial sites.
+So we chose our topic to build our own industrial data and apply search-based algorithms.
+
+Section 2 introduces the related paper about our topic. Section 3 introduces the basic model of the NRP problem that we are currently dealing with in our report.
+
+We divided the main part of the report into two parts.
+First, in section 4, we will organize the requirements in the actual product and create a dataset.
+And in this process, we're not going to use any random variables, and we're not going to bring in actual profit and cost from the future.
+And in Section 5, we're going to apply different search-based algorithms to the datasets that we've created.
+In addition to SA, GA, and NSGA2, which were introduced in class, we also implemented IPH and AHP directly and applied them to datasets.
+We will apply them to actual datasets and compare the performance of each algorithm in terms of time cost and optimization answers.
+And we'll also see how much search-based algorithm has increased the propitization compared to the actual true value.
+
+All codes used in the paper can be found at
+
+https://github.com/shkevinlee/CS454
 

### 2018-12-17 PaperBody.tex
add section4 subsection
Updates from ShareLaTeX

--- 2018-12-16 PaperBody.tex
@@
 
+\subsection{greedy algorithm}
+
 \subsection{Analytic Hierarchy Process}
+The Analytic Hierarchy Process(AHP) which was first applied to requirement prioritization by Karlsson and Ryan\cite{AHP} is a structured technique for organizing and analyzing complex decisions.
+To use the AHP for decision making, we have to perform pairwise comparisons of all the requirements to get their relative intensity.
+However, in our case, we cannot compare relatively each other and evaluate.
+Therefore, we define the relative intensity as the ratio of each requirement.
+
+\begin{algorithm}
+\caption{Analytic Hierarchy Process (AHP)}\label{alg:AHP}
+\begin{algorithmic}
+    \State $x \gets$ initial decision vector ;
+    \State $T \gets$ initial temperature ; 
+    \While{not stopping condition}
+        \State $x_{new} \gets GetRandomNeigbour(x)$ ;
+        \If {$AcceptanceRate(F(x), F(x_{new}), T) \geq random(0, 1)$}
+            \State $x \gets x_{new}$ ;
+        \EndIf
+        \State $T \gets COOL(T)$ \Comment{Lundy and Mess}
+    \EndWhile
+    \textbf{return} $x$
+\end{algorithmic}
+\end{algorithm}
 
@@
 
+The main loop of SA can be described in Algorithm \ref{alg:SA}. To increase the performance, we used a greedy solution as the initial decision vector.
+
 In our project, the parameter $\lambda$ and $\beta$ were set to 5 and $1 \times 10^{-8}$ since Bagnall et al. got the best solution for this value in their paper.
 
+\begin{algorithm}
+\caption{Simulated Annealing (SA)}\label{alg:SA}
+\begin{algorithmic}
+    \State $x \gets$ initial decision vector ;
+    \State $T \gets$ initial temperature ; 
+    \While{not stopping condition}
+        \State $x_{new} \gets GetRandomNeigbour(x)$ ;
+        \If {$AcceptanceRate(F(x), F(x_{new}), T) \geq random(0, 1)$}
+            \State $x \gets x_{new}$ ;
+        \EndIf
+        \State $T \gets COOL(T)$ \Comment{Lundy and Mess}
+    \EndWhile
+    \textbf{return} $x$
+\end{algorithmic}
+\end{algorithm}
+
 \subsection{Genetic Algorithm}
+The Genetic Algorithm(GA) is one of the evolutionary algorithms.
+In our project, we used a single objective function for GA which is the same with the simulated annealing.
+To make offspring population, we used the tournament selection, cross-over, and mutation operator.
+We also let the best one which has the best profit remain on the population for elitism.
 
 \subsection{NSGA-II}
+The Non-dominated Sorting Genetic Algorithm-II (NSGA-II) was introduced by Deb et al.\cite{NSGA2} It is one of the various approaches to solve the Multi-Objective Optimization Problems(MOOPs).
+So, to apply this algorithm, we have to decide the second objective function.
+
+The goal of our project is finding the optimal decision vector under the limited budget.
+Therefore, if we convert this single objective function into the MOOPs, our objective functions on MOOPs can be written as below:
+
+\[
+maximize \sum_{i = 1}^{N} profit_i \cdot x_i
+\]
+\[
+maximize -\sum_{i = 1}^{N} cost_i \cdot x_i
+\]
+
+The result of NSGA-II is the Pareto front on two objective function space.
+So, to get the optimal decision vector among them, we selected one which has maximum profits under the limited budget among the Pareto front.
+
+The main loop of NSGA-II can be described in Algorithm \ref{alg:nsga2}.
+Initial population is randomly created except one which is greedy solution.
+The \textit{make-new-pop} function consist of tournament selection, cross-over, and mutation operator which are used to create a child population.
 
@@
 \begin{algorithmic}
+    \State $t = 0$ ;
+    \State $P_0 \gets$ initial population ;
+    \State $Q_0 =$ make-new-pop($P_0$) ;
     \While{not stopping condition}
@@
         \State Let $t = t + 1$ ;
-    \EndWhile\label{euclidendwhile}
+    \EndWhile
 \end{algorithmic}
@@
     GA&3793.5045&13662.38600&16303.0&28522.11861 \\
-    NSGA-II&3822.47741&13700.52067&16518.33333&28729.33476 \\
+    NSGA-II&3822.47741&13700.52067&16332.6667&28729.33476 \\
     ILP&3825.42768&13768.44722&16336.0&28845.23124 \\
@@
 
-\begin{figure*}[h]
-\begin{subfigure}{\columnwidth}
-\includegraphics[width=0.9\linewidth]{SA-correlation.JPG}
-\caption{SA}
-\label{fig:subim5}
-\end{subfigure}
-\begin{subfigure}{\columnwidth}
-\includegraphics[width=0.9\linewidth]{GA-correlation.JPG}
-\caption{GA}
-\label{fig:subim6}
-\end{subfigure}
-\begin{subfigure}{\columnwidth}
-\includegraphics[width=0.9\linewidth]{ILP-correlation.JPG}
-\caption{ILP}
-\label{fig:subim7}
-\end{subfigure}
-\begin{subfigure}{\columnwidth}
-\includegraphics[width=0.9\linewidth]{AHP-correlation.JPG}
-\caption{AHP}
-\label{fig:subim8}
-\end{subfigure}
+%\begin{figure*}[h]
+%\begin{subfigure}{\columnwidth}
+%\includegraphics[width=0.9\linewidth]{SA-correlation.JPG}
+%\caption{SA}
+%\label{fig:subim5}
+%\end{subfigure}
+%\begin{subfigure}{\columnwidth}
+%\includegraphics[width=0.9\linewidth]{GA-correlation.JPG}
+%\caption{GA}
+%\label{fig:subim6}
+%\end{subfigure}
+%\begin{subfigure}{\columnwidth}
+%\includegraphics[width=0.9\linewidth]{ILP-correlation.JPG}
+%\caption{ILP}
+%\label{fig:subim7}
+%\end{subfigure}
+%\begin{subfigure}{\columnwidth}
+%\includegraphics[width=0.9\linewidth]{AHP-correlation.JPG}
+%\caption{AHP}
+%\label{fig:subim8}
+%\end{subfigure}
 
-\caption{Cost-Profit Correlation}
-\label{fig:image2}
-\end{figure*}
+%\caption{Cost-Profit Correlation}
+%\label{fig:image2}
+%\end{figure*}
+
+\begin{table*}[]
+\caption{The sum of profits on each limited budget}
+\begin{tabular}{@{}llllll@{}}
+\toprule
+\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6}
+\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{AHP} & \multicolumn{1}{c}{ILP} & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} \\ \midrule
+100,000 & 14472.21303& \textbf{14530.92923}& 13787.94014& 13916.62496& 14359.51809\\
+120,000 & 16798.95935& \textbf{16845.48739}& 16269.28033& 16440.60658& 16746.14339\\
+140,000 & 18948.3466&  \textbf{18979.35023}& 18553.36746& 18706.04924& 18906.95215\\
+160,000 & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\
+180,000 & 22683.10701& \textbf{22718.92665}& 22332.52554& 22449.04724& 22651.51132\\
+200,000 & 24343.18852& \textbf{24369.86106}& 23894.25792& 24054.60654& 24281.04096\\
+220,000 & 25881.1836&  \textbf{25901.23028}& 25425.18545& 25565.45349& 25804.51079\\
+240,000 & 27305.09756& \textbf{27324.51067}& 26790.58789& 26987.08126& 27214.27095\\
+260,000 & 28626.58769& \textbf{28653.54334}& 28161.5672&  28293.21833& 28556.63614\\ \bottomrule
+\end{tabular}
+\end{table*}
 
 \begin{figure*}[h]
-\includegraphics[width=0.9\linewidth]{cost-profit-together.JPG}
+\includegraphics[width=0.9\linewidth]{ParetoFronts.png}
 \caption{Cost-Profit Correlation in one graph}
-\label{fig:image3}
+\label{fig:paretofronts}
 \end{figure*}

### 2018-12-17 PaperBody.tex

@@
 for some bound $B \in \mathbb{Z}^+$ which represents the limited budget.
+
+\section{Data sets}
+
+\subsection{Bugzilla}
+\subsection{Open Source repository}
+\subsection{Crawling Modeling}
+\subsection{Research Question}
+\subsection{Profit}
+\subsection{Cost}
 

### 2018-12-17 PaperBody.tex
graph and result edited

@@
 Except ILP and AHP, maximum profit is high in order of NSGA-II, GA, then SA.
-Peculiar thing is that, in dataset \textit{bugzilla-firefox-priority-2016meancost}, NSGA-II is largely bigger than other four algorithms.
-The reason we suppose is that other three datasets' profit is variety because the number of comments is not bounded, but this dataset's profit is priority, which is varied only in 1, 2, 3, 4, and 5 points.
-In this case, requirements can be seen more similar each other than other datasets.
-This difference could influence the difference of the result.\\
+\\
 At experiment 2, we applied four algorithms except NSGA-II to dataset \textit{bugzilla-firefox-comments+priority-2016meancost}.

### 2018-12-17 PaperBody.tex
Updates from ShareLaTeX

--- 2018-12-17 PaperBody.tex
@@
 \section{Introduction}
- The NRP problem is the choice of what requirements the company will reflect when making the next version of the product.
+ The Next Release Problem(NRP) is the choice of what requirements the company will reflect when making the next version of the product.
 This problem is primarily aimed at helping the company get the most profit from limited costs.
@@
  We point out that these processes are wrong.
-The real NRP problem is that the cost and profit are not independent, and because it is used in the real industry, the process of obtaining the cost and profit has to be included to entire process.
+The real NRP is that the cost and profit are not independent, and because it is used in the real industry, the process of obtaining the cost and profit has to be included to entire process.
 Also, importing and writing data from the future makes it difficult for research results to be applied to actual industrial sites.
@@
 We will apply them to actual datasets and compare the performance of each algorithm in terms of time cost and optimization answers.
-And we'll also see how much search-based algorithm has increased the propitization compared to the actual true value.
+And we'll also see how much search-based algorithm has increased the profit compared to the actual true value.
 
-All codes used in the paper can be found at
-
-https://github.com/shkevinlee/CS454
+All codes used in the paper can be found at https://github.com/shkevinlee/CS454
 
@@
 \begin{subfigure}{\columnwidth}
-\includegraphics[width=0.9\linewidth]{bugzilla_firefox_priority_2016meancost.JPG}
+\includegraphics[width=0.9\linewidth]{bugzilla_firefox_log(comments)_2016meancost.JPG}
 \caption{bugzilla-firefox-priority-2016meancost}

### 2018-12-17 PaperTitle.tex
Updates from ShareLaTeX

@@
 \usepackage{subcaption}
+\usepackage{pgfplots}
+\usepackage{multirow}
 
@@
 \email{tardis_95@kaist.ac.kr}
+\email{qodudrud(github)}
 
@@
 \email{hiall21@kaist.ac.kr}
+\email{hiall21(github)}
 
@@
 \begin{abstract}
-This report provides the work of applying NRP problems to real-world problem.
-The NRP problem is where the company chooses which requirements to reflect when releasing the next version.
+This report provides the work of applying NRP to real-world problem.
+The NRP is where the company chooses which requirements to reflect when releasing the next version.
 We criticize the fact that most of the previous papers extracted results using random variables rather than actual data values.
 To improve that, we've taken the data out of the Bugzilla in Firefox and Eclipse repositories, and we've solved the problem of choosing which bugs need to be fixed in the next version.
-We compared performance by applying several known algorithms, SA, GA NSGA2, IHP, and AHP.
+We compared performance by applying several known algorithms, SA, GA, NSGA2, ILP, and AHP.
 This report shows how well the application of search-based algorithms to NRP problems in the real world, and which algorithms are the most effective.

### 2018-12-17 PaperBody.tex
Experimental set up added

@@
 And in Section 5, we're going to apply different search-based algorithms to the datasets that we've created.
-In addition to SA, GA, and NSGA2, which were introduced in class, we also implemented IPH and AHP directly and applied them to datasets.
+In addition to SA, GA, and NSGA2, we also implemented ILH and AHP directly and applied them to datasets.
 We will apply them to actual datasets and compare the performance of each algorithm in terms of time cost and optimization answers.
@@
 
-All codes used in the paper can be found at https://github.com/shkevinlee/CS454
+All codes used in the paper can be found at
+
+https://github.com/shkevinlee/CS454
 
@@
 The company always wants to select requirements for the next release to get the highest sum of profits in the limited budget.
-Let the decision vector $x = \{x_1, x_2, \ldots, x_n\} \in \{0, 1\}$ where $x_i$ is 1 if requirement $i$ is selected and 0 otherwise.
+Let the decision vector $\textbf{x} = \{x_1, x_2, \ldots, x_n\} \in \{0, 1\}$ where $x_i$ is 1 if requirement $i$ is selected and 0 otherwise.
 Then our objective function can be written as below:
@@
 \section{Algorithms}
-We applied two deterministic algorithms(AHP and ILP) and three heuristic algorithms(SA, GA and NSGA-II) which were introduced as the algorithms well-suited for the NRP in papers.\cite{NRP}\cite{ILP}\cite{IGA}\cite{MONRP}
+We applied two deterministic algorithms(AHP and ILP) and three heuristic algorithms(SA, GA and NSGA-II) which were introduced as the algorithms well-suited for the NRP in papers\cite{NRP}\cite{ILP}\cite{IGA}\cite{MONRP}.
+And, to encourage the performance of heuristic algorithms, we put a greedy solution into the initial population or initial decision vector.
 
-\subsection{greedy algorithm}
+The greedy algorithm for the initial solution of heuristic algorithms is described as below.
+
+\begin{algorithm}
+\caption{greedy algorithm}\label{alg:greedy}
+\begin{algorithmic}
+    \State Let $\textbf{x} = \{0, 0, \ldots, 0\}$ ;
+    \State Let $CostSum = 0$ ;
+    \For{$i = 1$ to $N$}
+        \State $p = argmax(Profit)$ ;
+        \If {$CostSum + cost_p \leq B$}
+            \State $x_p = 1$ ;
+            \State $CostSum = CostSum + cost_p$ ;
+        \EndIf
+        \State $profit_p = -\infty$ ;
+    \EndFor
+    \textbf{return} $x$
+\end{algorithmic}
+\end{algorithm}
 
@@
     \midrule
-    Real Cost&50699.70190&262945.49581&262945.49581&262945.49581 \\
+    Estimated Cost&50699.70190&262945.49581&262945.49581&262945.49581 \\
     Real Profit&3489.63592&13025.88085&12210&26332.88085 \\
@@
     NSGA-II&3822.47741&13700.52067&16332.6667&28729.33476 \\
-    ILP&3825.42768&13768.44722&16336.0&28845.23124 \\
+    ILP& \textbf{3825.42768}&\textbf{13768.44722}&\textbf{16336.0}&\textbf{28845.23124} \\
     AHP&3810.3125825&13758.5577962&16249.0&28811.2749907 \\
@@
   \end{tabular}
+\label{table:DatasetProfit}
 \end{table*}
@@
 \begin{subfigure}{\columnwidth}
-\includegraphics[width=0.9\linewidth]{bugzilla_firefox_log(comments)_2016meancost.JPG}
+\includegraphics[width=0.9\linewidth]{bugzilla_firefox_priority_2016meancost.JPG}
 \caption{bugzilla-firefox-priority-2016meancost}
@@
 \caption{Profit Comparison for each dataset}
-\label{fig:image1}
+\label{fig:DatasetProfit}
 \end{figure*}
@@
 \begin{table*}[]
-\caption{The sum of profits on each limited budget}
+\caption{Profit on each limited budget}
 \begin{tabular}{@{}llllll@{}}
@@
 \end{tabular}
+\label{table:ParetoFront}
 \end{table*}
@@
 
-\section{Results}
+\section{Experimental Set up}
+In this section, we describe two experiments for comparing algorithms on datasets and analyzing correlation between cost and profit.
+We used four datasets(\textit{eclipse, firefox-I, firefox-II} and \textit{firefox-III}) from Bugzilla on experiments which were described in \textbf{section 4}.
+
+At first experiment(EX1), we applied each algorithm to four datasets in order to compare their performances.
+And we hope to know the effect by different profit strategies through analyzing \textit{firefox-I}, \textit{firefox-II}, and \textit{firefox-III} dataset.
+
+At second experiment(EX2), we applied each algorithm to \textit{firefox-III} dataset to analyze the correlation between cost and profit.
+And also, we expected to get the interesting range which have a great change as the limted budget are increased or decreased.
+
+All heuristic approaches(SA, GA and NSGA-II) were run for 500,000 function evaluations.
+The population size was set to 200.
+So each experimental execution of GA and NSGA-II was terminated when the generation number reached 2,500.
+GA and NSGA-II used the tournament selection(tournament size is 5), single-point cross-over, and bit-wise mutation for binary-coded GAs.
+The cross-over probability and the mutation probability were set to 0.8 and 1/N (where N is the length of chromosome same with the number of requirements).
+
+\section{Result and Analysis}
 At first experiment, we applied five algorithms to four datasets and compared the maximum profit each other.
-In \textbf{table 1}, upper two rows are real cost sum and real profit sum of each datasets.
-Below these rows, there are maximum profits for each algorithms in four datasets.
-At the result, every maximum profits are bigger than real profit sum.
+In \textbf{table \ref{table:DatasetProfit}}, upper two rows are estimated cost sum and real profit sum of each datasets.
+Below these rows, there are averaged profits for each algorithms on four datasets.
+At the result, every profits for algorithms are bigger than real profit sum.
 Also, consumed time to return maximum profit was exceedingly short in ILP and AHP, rather than SA, GA, and NSGA-II.
-\\
-\textbf{Figure 1} is the graphs of \textbf{table 1}.
-Each graph expresses the maximum profit of five algorithms.
-At the result, the maximum profit of ILP is the biggest, and the maximum profit of NSGA-II and AHP is bigger than the maximum profit of SA and GA in most case.
+
+\textbf{Figure \ref{fig:DatasetProfit}} is the graphs of \textbf{table 1}.
+Each graph expresses the averaged profit of five algorithms.
+At the result, the profit of ILP is the biggest, and the profit of NSGA-II and AHP is bigger than SA and GA in most case.
 Except ILP and AHP, maximum profit is high in order of NSGA-II, GA, then SA.
-\\
-At experiment 2, we applied four algorithms except NSGA-II to dataset \textit{bugzilla-firefox-comments+priority-2016meancost}.
-At this experiment, we got the maximum profits while changing the cost constraints.
-The result is expressed in \textbf{Figure 2} and \textbf{Figure 3}.
-\textbf{Figure 2} expresses maximum profits on each cost, and \textbf{Figure 3} is integrating graph of \textbf{Figure 2} because of comparing the difference for four algorithms.
-\\
-The result is that they are all increasing almost linearly and similarly.
+
+At experiment 2, we got the profits while changing the cost constraint.
+The result is expressed in \textbf{Figure \ref{fig:paretofronts}}.
+\textbf{Figure \ref{fig:paretofronts}} expresses maximum profits on each cost, and \textbf{Figure 3} is integrating graph of \textbf{Figure 2} because of comparing the difference for four algorithms.
+
+The result is that they are all increasing almost similarly.
 One of the reasons to perform this experiment was that we wondered if there is a peculiar part in cost-profit graph.(if there is exceeding increase in profit) And at the result, there is no prominently peculiar part, and all the results are increasing normally.
+
 \section{Conclusion}

### 2018-12-17 PaperBody.tex
Experimental set up edited
add Conclusion and AHP 1 line

@@
 Therefore, we define the relative intensity as the ratio of each requirement.
+Then we will sort the ratio and selected the requirements so that they would not exceed the limited cost.
 
@@
 All heuristic approaches(SA, GA and NSGA-II) were run for 500,000 function evaluations.
+SA started from a greedy solution and GA and NSGA-II started from the initial population which contains a greedy solution.
 The population size was set to 200.
@@
 \section{Conclusion}
+The research question we presented was two things.
+The RQ1.
+"Could we estimate profit from Bugzilla without forward looking?".
+We were able to get a proposal for the demand of custmers in Bugzilla through Priority and Comment.
+The RQ2.
+"Could we estimate profit from Bugzilla without forward looking?".
+We define the Cost in Bugzilla as time.
+The component's Cost is not accurate.
+However, the costs are not meaningless given the trends of 2016 and 2017.
+With this research question, we have built a dataset in the real world for NRP research.
+
+In the results of the experiment.
+EX1.
+was profit comparison.
+Exept for dataset with priority, the ILP has the highest result.
+And deterministic algorithms that AHP and ILP are very fast than heuristic algorithms.
+Ex2.
+is a comparison of the results of the profit according to the cost limit.
+As we mentioned, we found that limits of the Cost and the Profit had a linear relationship, regardless of algorithm.
+These results show that tere are no major problems with applying NRP argorithms to our dataset.
+Therefore, the dataset was well set to solve  the NRP.
+
+In previous NRP studies, both dataset were applied with the random Cost and Profit values.
+But our project use actual situations value.
+It also showed that the NRP's algorithm worked well.
+In this way, later NRP studies have shown the possibility of using real situations rather than random values.

### 2018-12-17 PaperBody.tex
Updates from ShareLaTeX

--- 2018-12-17 PaperBody.tex
@@
 \section{Data sets}
+
+\begin{table} [H]
+  \caption{Dataset from Bugzilla}
+  \label{tab:commands}
+  \begin{tabular}{cccccl}
+    \toprule
+    &ECLIPSE&FIREFOX-I&FIREFOX-II&FIREFOX-III\\
+    \midrule
+    Cost& 50699.70& 262945.50& 262945.50& 262945.50 \\
+    Profit& 3489.64& 13025.88& 12210& 26332.88 \\
+    \bottomrule
+  \end{tabular}
+\label{table:Dataset}
+\end{table}
 
@@
 
-\begin{table*}
-  \caption{Profit Comparison}
-  \label{tab:commands}
-  \begin{tabular}{cccccl}
-    \toprule
-    &eclipse-log&firefox-log&firefox-priority&firefox-comments+priority\\
-    \midrule
-    Estimated Cost&50699.70190&262945.49581&262945.49581&262945.49581 \\
-    Real Profit&3489.63592&13025.88085&12210&26332.88085 \\
-    \hline
-    SA&3702.85182&13524.93411&16300.0&28358.2295685 \\
-    GA&3793.5045&13662.38600&16303.0&28522.11861 \\
-    NSGA-II&3822.47741&13700.52067&16332.6667&28729.33476 \\
-    ILP& \textbf{3825.42768}&\textbf{13768.44722}&\textbf{16336.0}&\textbf{28845.23124} \\
-    AHP&3810.3125825&13758.5577962&16249.0&28811.2749907 \\
-    \bottomrule
-  \end{tabular}
-\label{table:DatasetProfit}
-\end{table*}
+%\begin{table*}
+%  \caption{Profit Comparison}
+%  \label{tab:commands}
+%  \begin{tabular}{cccccl}
+%    \toprule
+%    &eclipse&firefox-I&firefox-II&firefox-III\\
+%    \midrule
+%    Estimated Cost&50699.70190&262945.49581&262945.49581&262945.49581 \\
+%    Real Profit&3489.63592&13025.88085&12210&26332.88085 \\
+%    \hline
+%    SA&3702.85182&13524.93411&16300.0&28358.2295685 \\
+%    GA&3793.5045&13662.38600&16303.0&28522.11861 \\
+%    NSGA-II&3822.47741&13700.52067&16332.6667&28729.33476 \\
+%    ILP& \textbf{3825.42768}&\textbf{13768.44722}&\textbf{16336.0}&\textbf{28%845.23124} \\
+%    AHP&3810.3125825&13758.5577962&16249.0&28811.2749907 \\
+%    \bottomrule
+%  \end{tabular}
+%\label{table:DatasetProfit}
+%\end{table*}
 % end the environment with {table*}, NOTE not {table}!
@@
 \includegraphics[width=0.9\linewidth]{bugzilla_eclipse_log(comments)_2016meancost.JPG}
-\caption{bugzilla-eclipse-log(comments)-2016meancost}
-\label{fig:subim1}
+\caption{ECLIPSE dataset. \normalfont{The estimated cost is 50699.70190}}
 \end{subfigure}
@@
 \includegraphics[width=0.9\linewidth]{bugzilla_firefox_log(comments)_2016meancost.JPG}
-\caption{bugzilla-firefox-log(comments)-2016meancost}
-\label{fig:subim2}
+\caption{FIREFOX-I. \normalfont{The estimated cost is 262945.49581}}
 \end{subfigure}
@@
 \includegraphics[width=0.9\linewidth]{bugzilla_firefox_priority_2016meancost.JPG}
-\caption{bugzilla-firefox-priority-2016meancost}
-\label{fig:subim3}
+\caption{FIREFOX-II. \normalfont{The estimated cost is 262945.49581}}
 \end{subfigure}
@@
 \includegraphics[width=0.9\linewidth]{bugzilla_firefox_comments-priority_2016meancost.JPG}
-\caption{bugzilla-firefox-comments+priority-2016meancost}
-\label{fig:subim4}
+\caption{FIREFOX-III. \normalfont{The estimated cost is 262945.49581}}
 \end{subfigure}
@@
 \caption{Profit on each limited budget}
-\begin{tabular}{@{}llllll@{}}
+\begin{tabular}{@{}crrrrr@{}}
 \toprule
@@
 In this section, we describe two experiments for comparing algorithms on datasets and analyzing correlation between cost and profit.
-We used four datasets(\textit{eclipse, firefox-I, firefox-II} and \textit{firefox-III}) from Bugzilla on experiments which were described in \textbf{section 4}.
+We used four datasets(\textit{ECLIPSE, FIREFOX-I, FIREFOX-II} and \textit{FIREFOX-III}) from Bugzilla on experiments which were described in \textbf{section 4}.
 
 At first experiment(EX1), we applied each algorithm to four datasets in order to compare their performances.
-And we hope to know the effect by different profit strategies through analyzing \textit{firefox-I}, \textit{firefox-II}, and \textit{firefox-III} dataset.
+And we hope to know the effect by different profit strategies through analyzing \textit{FIREFOX-I}, \textit{FIREFOX-II}, and \textit{FIREFOX-III} dataset.
 
-At second experiment(EX2), we applied each algorithm to \textit{firefox-III} dataset to analyze the correlation between cost and profit.
-And also, we expected to get the interesting range which have a great change as the limted budget are increased or decreased.
+At second experiment(EX2), we applied each algorithm to \textit{FIREFOX-III} dataset to analyze the correlation between cost and profit.
+And also, we expected to get the interesting range which have a great change as the limited budget are increased or decreased.
 
 All heuristic approaches(SA, GA and NSGA-II) were run for 500,000 function evaluations.
+SA started from a greedy solution and GA and NSGA-II started from the initial population which contains a greedy solution.
 The population size was set to 200.
@@
 The cross-over probability and the mutation probability were set to 0.8 and 1/N (where N is the length of chromosome same with the number of requirements).
+Every heuristic algorithms were executed 3 times for each experiment.
 
 \section{Result and Analysis}
+\subsection{Experiment 1}
+At EX1, we applied two deterministic and three heuristic algorithms to four datasets and compared the averaged profit to each other.
+Figure \ref{fig:DatasetProfit} shows the results of EX1.
+Each graph expresses the averaged profit of five algorithms under the limited budget(or the estimated cost).
+
+In these results, the averaged profit of each algorithm were bigger than the real profit in Table \ref{table:Dataset}.
+In every case, the ILP has the biggest profit.
+However, the order of other algorithms are slightly changed for dataset.
+
+The SA has the smallest profit in most cases, except Figure \ref{fig:DatasetProfit}-(c). We thought that the reason of that are due to its too slow convergence.
+
+\subsection{Experiment 2}
+
 At first experiment, we applied five algorithms to four datasets and compared the maximum profit each other.
-In \textbf{table \ref{table:DatasetProfit}}, upper two rows are estimated cost sum and real profit sum of each datasets.
+In \textbf{Table \ref{table:DatasetProfit}}, upper two rows are estimated cost sum and real profit sum of each datasets.
 Below these rows, there are averaged profits for each algorithms on four datasets.

### 2018-12-17 PaperBody.tex
Updates from ShareLaTeX

--- 2018-12-17 PaperBody.tex
@@
 \section{Data sets}
+    We tried to implement a dataset in the real industry.
+\subsection{Bugzilla}
 
-\subsection{Bugzilla}
+    We chose Bugzilla where we could get the data source.
+
+Bugzilla is a web-based, general purpose bug tracker and test tool originally developed and used by the Mozilla project.
+When users or developers report bugs to the repository for each project in Bugzilla, the project manager or the developer in charge identifies them, reflects them on the product, or re-prioritizes them.
+
+The biggest reason for choosing Bugzilla is that all the data is open.
+The actual requirements normally are not disclosed for security reasons.
+However, all the data is open because Bugzilla has to report on the bug.
+It also contains a number of data that can be used to estimates the cost and profit.
+The most recent version was announced in the 15th year, and many open sources, including the Mozilla Project, are actively using bug tracking.
+
+Here are some of the Bugzilla sites in operation.
+
+Mozilla -https://bugzilla.mozilla.org/
+
+Eclipse - https://bugs.eclipse.org/bugs/
+
+We can assume that one bug is a requirement. And once you've solved this bug report, you can think of it as reflected in the next version.
+
 \subsection{Open Source repository}
@@
 Therefore, we define the relative intensity as the ratio of each requirement.
-Then we will sort the ratio and selected the requirements so that they would not exceed the limited cost.
 
@@
 \section{Conclusion}
-The research question we presented was two things.
-The RQ1.
-"Could we estimate profit from Bugzilla without forward looking?".
-We were able to get a proposal for the demand of custmers in Bugzilla through Priority and Comment.
-The RQ2.
-"Could we estimate profit from Bugzilla without forward looking?".
-We define the Cost in Bugzilla as time.
-The component's Cost is not accurate.
-However, the costs are not meaningless given the trends of 2016 and 2017.
-With this research question, we have built a dataset in the real world for NRP research.
-
-In the results of the experiment.
-EX1.
-was profit comparison.
-Exept for dataset with priority, the ILP has the highest result.
-And deterministic algorithms that AHP and ILP are very fast than heuristic algorithms.
-Ex2.
-is a comparison of the results of the profit according to the cost limit.
-As we mentioned, we found that limits of the Cost and the Profit had a linear relationship, regardless of algorithm.
-These results show that tere are no major problems with applying NRP argorithms to our dataset.
-Therefore, the dataset was well set to solve  the NRP.
-
-In previous NRP studies, both dataset were applied with the random Cost and Profit values.
-But our project use actual situations value.
-It also showed that the NRP's algorithm worked well.
-In this way, later NRP studies have shown the possibility of using real situations rather than random values.

### 2018-12-17 PaperBody.tex
dataset on progressing

--- 2018-12-17 PaperBody.tex
@@
 \section{Data sets}
+We tried to implement a dataset in the real industry.
+
+\subsection{Bugzilla}
+
+We chose Bugzilla where we could get the data source.
+
+Bugzilla is a web-based, general purpose bug tracker and test tool originally developed and used by the Mozilla project.
+When users or developers report bugs to the repository for each project in Bugzilla, the project manager or the developer in charge identifies them, reflects them on the product, or re-prioritizes them.
+
+The biggest reason for choosing Bugzilla is that all the data is open.
+The actual requirements normally are not disclosed for security reasons.
+However, all the data is open because Bugzilla has to report on the bug.
+It also contains a number of data that can be used to estimates the cost and profit.
+The most recent version was announced in the 15th year, and many open sources, including the Mozilla Project, are actively using bug tracking.
+
+Here are some of the Bugzilla sites in operation.
+
+\textbf{Mozilla} -\textit{https://bugzilla.mozilla.org/}
+
+\textbf{Eclipse} -\textit{ https://bugs.eclipse.org/bugs/}
+
+We can assume that one bug is a requirement. And once you've solved this bug report, you can think of it as reflected in the next version.
+
+\subsection{Open Source repository}
+
+Now many open sources are actively using Bugzilla.
+We chose two of the most famous open sources, Firefox and Eclipse.
+Each repository consists of several platforms inside the open source.
+We decided to extract data from the two platforms where the most bugs were resolved in 2017.
+The \textbf{Firefox Web browser} platform was selected in the Firefox repository, and the \textbf{Eclipse platform} was selected in the Eclipse repository.
+
+\subsection{Crawling Modeling}
+
+We decided to create a dataset based on data from 2017.
+The reason is that if too many previous years of data are used, unresolved bugs are more likely to be reported incorrectly or missing than being pushed out of the priority list.
+Also, for real value comparison, we  needed some time to solve the bug, so we targeted 2017.
+
+It's a little bit difficult to apply them right into the NRP problem because they're being reflected in the product in real time deployment. So we extract the data set based on a few assumptions:
+
+\textbf{Requirements for 2017} : 2017. 1. 1. 00:00 to 2017. 12. 31 59:59 The issues registered in 2017 but not resolved shall be considered as requirements for products.
+
+\textbf{Bugs Resolved in 2018 (true value)}: In the 2017 requirement, they are considered to be the requirements reflected in the next version of the actual product are considered.
+
+The results of our target project are as follows table1
+\begin{table} [H]
+  \caption{Number of requirements}
+  \label{tab:commands}
+  \begin{tabular}{cccccl}
+    \toprule
+    &ECLIPSE PLATFORM&FIREFOX BROWSER\\
+    \midrule
+    Reported in 2017& 1 & 1 \\
+    Resolved in 2018 & 1&1 \\
+    \bottomrule
+  \end{tabular}
+\label{table:Dataset}
+\end{table}
+
+\subsection{Research Question}
+\subsection{Profit}
+\subsection{Cost}
 
@@
 \end{table}
-
-\subsection{Bugzilla}
-\subsection{Open Source repository}
-\subsection{Crawling Modeling}
-\subsection{Research Question}
-\subsection{Profit}
-\subsection{Cost}
 

### 2018-12-17 PaperBody.tex
Updates from ShareLaTeX

--- 2018-12-17 PaperBody.tex
@@
 The Analytic Hierarchy Process(AHP) which was first applied to requirement prioritization by Karlsson and Ryan\cite{AHP} is a structured technique for organizing and analyzing complex decisions.
-To use the AHP for decision making, we have to perform pairwise comparisons of all the requirements to get their relative intensity.
-However, in our case, we cannot compare relatively each other and evaluate.
-Therefore, we define the relative intensity as the ratio of each requirement.
-Then we will sort the ratio and selected the requirements so that they would not exceed the limited cost.
-
-\begin{algorithm}
-\caption{Analytic Hierarchy Process (AHP)}\label{alg:AHP}
-\begin{algorithmic}
-    \State $x \gets$ initial decision vector ;
-    \State $T \gets$ initial temperature ; 
-    \While{not stopping condition}
-        \State $x_{new} \gets GetRandomNeigbour(x)$ ;
-        \If {$AcceptanceRate(F(x), F(x_{new}), T) \geq random(0, 1)$}
-            \State $x \gets x_{new}$ ;
-        \EndIf
-        \State $T \gets COOL(T)$ \Comment{Lundy and Mess}
-    \EndWhile
-    \textbf{return} $x$
-\end{algorithmic}
-\end{algorithm}
+To use the AHP for decision making in general, we had to perform pairwise comparisons of all the requirements to get their relative intensity.
+But, in our case, we don't have to compare relatively each other since each requirements has its own profit and cost.
+Therefore, we defined the relative intensity as the ratio of each requirement and made the profit-comparison matrix and the cost-comparison matrix by using them.
+And then, we calculated the priority vector.
+To get the optimal decision vector, we sorted the priority vector by its weight and selected requirements while the sum of costs didn't exceed the limited budget.
 
@@
 
-\begin{table*}[]
-\caption{Profit on each limited budget}
-\begin{tabular}{@{}crrrrr@{}}
-\toprule
-\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6}
-\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{AHP} & \multicolumn{1}{c}{ILP} & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} \\ \midrule
-100,000 & 14472.21303& \textbf{14530.92923}& 13787.94014& 13916.62496& 14359.51809\\
-120,000 & 16798.95935& \textbf{16845.48739}& 16269.28033& 16440.60658& 16746.14339\\
-140,000 & 18948.3466&  \textbf{18979.35023}& 18553.36746& 18706.04924& 18906.95215\\
-160,000 & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\
-180,000 & 22683.10701& \textbf{22718.92665}& 22332.52554& 22449.04724& 22651.51132\\
-200,000 & 24343.18852& \textbf{24369.86106}& 23894.25792& 24054.60654& 24281.04096\\
-220,000 & 25881.1836&  \textbf{25901.23028}& 25425.18545& 25565.45349& 25804.51079\\
-240,000 & 27305.09756& \textbf{27324.51067}& 26790.58789& 26987.08126& 27214.27095\\
-260,000 & 28626.58769& \textbf{28653.54334}& 28161.5672&  28293.21833& 28556.63614\\ \bottomrule
-\end{tabular}
-\label{table:ParetoFront}
-\end{table*}
-
-\begin{figure*}[h]
-\includegraphics[width=0.9\linewidth]{ParetoFronts.png}
-\caption{Cost-Profit Correlation in one graph}
-\label{fig:paretofronts}
-\end{figure*}
+%\begin{figure*}[h]
+%\includegraphics[width=0.9\linewidth]{ParetoFronts.png}
+%\caption{Cost-Profit Correlation in one graph}
+%\label{fig:paretofronts}
+%\end{figure*}
 
@@
 \section{Result and Analysis}
-\subsection{Experiment 1}
-At EX1, we applied two deterministic and three heuristic algorithms to four datasets and compared the averaged profit to each other.
-Figure \ref{fig:DatasetProfit} shows the results of EX1.
-Each graph expresses the averaged profit of five algorithms under the limited budget(or the estimated cost).
 
-In these results, the averaged profit of each algorithm were bigger than the real profit in Table \ref{table:Dataset}.
-In every case, the ILP has the biggest profit.
-However, the order of other algorithms are slightly changed for dataset.
-
-The SA has the smallest profit in most cases, except Figure \ref{fig:DatasetProfit}-(c). We thought that the reason of that are due to its too slow convergence.
-
-\subsection{Experiment 2}
-
-At first experiment, we applied five algorithms to four datasets and compared the maximum profit each other.
+%At first experiment, we applied five algorithms to four datasets and compared the maximum profit each other.
 In \textbf{Table \ref{table:DatasetProfit}}, upper two rows are estimated cost sum and real profit sum of each datasets.
@@
 
-\textbf{Figure \ref{fig:DatasetProfit}} is the graphs of \textbf{table 1}.
-Each graph expresses the averaged profit of five algorithms.
-At the result, the profit of ILP is the biggest, and the profit of NSGA-II and AHP is bigger than SA and GA in most case.
-Except ILP and AHP, maximum profit is high in order of NSGA-II, GA, then SA.
+%\textbf{Figure \ref{fig:DatasetProfit}} is the graphs of \textbf{table 1}.
+Each graph %expresses the averaged profit of five algorithms.
+At the result, the profit of ILP is %the biggest, and the profit of NSGA-II and AHP is bigger than SA and GA in most case.
+%Except ILP and AHP, maximum profit is high in order of NSGA-II, GA, then SA.
 
-At experiment 2, we got the profits while changing the cost constraint.
+%At experiment 2, we got the profits while changing the cost constraint.
 The result is expressed in \textbf{Figure \ref{fig:paretofronts}}.
@@
 
-The result is that they are all increasing almost similarly.
+%The result is that they are all increasing almost similarly.
 One of the reasons to perform this experiment was that we wondered if there is a peculiar part in cost-profit graph.(if there is exceeding increase in profit) And at the result, there is no prominently peculiar part, and all the results are increasing normally.
+
+\subsection{Experiment 1}
+At EX1, we applied two deterministic and three heuristic algorithms to four datasets and compared the averaged maximum profit to each other.
+Figure \ref{fig:DatasetProfit} shows the results of EX1.
+Each graph expresses the profit of five algorithms under the limited budget(= the estimated cost).
+
+In these results, the profit of each algorithm were bigger than the real profit in Table \ref{table:Dataset}.
+And, in every case, the ILP has the biggest profit.
+However, the order of other algorithms are slightly changed for dataset.
+
+The SA has the smallest profit in most cases, except Figure \ref{fig:DatasetProfit}-(c).
+Although the SA started from a greedy solution, there is little difference between the result and a greedy solution.
+The profit of GA is bigger than SA and smaller than NSGA-II in every cases.
+So, the profit is high in order of NSGA-II, GA, then SA.
+The AHP has good performances for some cases.
+However, it has the lowest profit in \ref{fig:DatasetProfit}-(c).
+Therefore, we can conclude that the strategy about evaluating profit can be affect the results.
+
+The run time of two deterministic algorithms were much faster than heuristic algorithms.
+Therefore, we can conclude that the ILP is well-suited for our datasets and also it is much faster than other heuristic algorithms.
+
+\subsection{Experiment 2}
+\begin{table*}[]
+\caption{Profit on each limited budget}
+\begin{tabular}{@{}crrrrr@{}}
+\toprule
+\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6}
+\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{AHP} & \multicolumn{1}{c}{ILP} & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} \\ \midrule
+100,000 & 14472.21303& \textbf{14530.92923}& 13787.94014& 13916.62496& 14359.51809\\
+120,000 & 16798.95935& \textbf{16845.48739}& 16269.28033& 16440.60658& 16746.14339\\
+140,000 & 18948.34660& \textbf{18979.35023}& 18553.36746& 18706.04924& 18906.95215\\
+160,000 & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\
+180,000 & 22683.10701& \textbf{22718.92665}& 22332.52554& 22449.04724& 22651.51132\\
+200,000 & 24343.18852& \textbf{24369.86106}& 23894.25792& 24054.60654& 24281.04096\\
+220,000 & 25881.18360& \textbf{25901.23028}& 25425.18545& 25565.45349& 25804.51079\\
+240,000 & 27305.09756& \textbf{27324.51067}& 26790.58789& 26987.08126& 27214.27095\\
+260,000 & 28626.58769& \textbf{28653.54334}& 28161.56720& 28293.21833& 28556.63614\\ \bottomrule
+\end{tabular}
+\label{table:ParetoFront}
+\end{table*}
+
+At EX2, we got the profits while changing the cost constraint.
+The result is expressed in Table \ref{table:ParetoFront}.
+In the results, profits of each algorithms are all increasing almost similarly and the order of profits(ILP, AHP.
+NSGA-II, GA, then SA) are same in every case.
+And also, we observed that the change of profits become smaller as the limited budget increases.
+
+One of the reasons to perform EX2 was that we wondered if there is a peculiar part in cost-profit graph. However, we cannot observe prominently peculiar part in the dataset.
 

### 2018-12-18 PaperBody.tex
Results are edited
Related work are edited
Profit done, cost on progressing

@@
 And also, they set the importance(or weight) of each customer who demands for resolving requirements to company.
+They applied several heuristic method(various versions of simulated annealing and hill climbers) and concluded that the simulated annealing algorithm found the best solutions using only modes amounts of computing time in their dataset.
 
@@
 \subsection{Research Question}
+
+We're trying to extract the estimated cost and profit values from the crawled dataset. Our research question can be divided into two main areas.
+
+\textbf{RQ1}. \textit{Could we estimate PROFIT from Bugzilla without Forward Looking?}
+
+\textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}
+
 \subsection{Profit}
+
+ Profit is an indicator of how much the value of the product has increased when the company has addressed this requirement. There were two indicators in Bugzilla that directly represented this value.
+
+\textbf{Priority}: Priority for bugs
+
+\textbf{Severity}: The Severity of the bug
+
+And there are other indicators that show interest in bugs.
+
+\textbf{Resolution, Votes, Number of Comments}
+
+Among these, the indicators with sufficient coverage of the data were \textit{Priority} and \textit{Number of comments}.
+The rest of the indicators were either underutilized by the project manager, or there was not much value difference between the requirements.
+
+\textbf{Priority}: In the case of priority, the manager directly ranks the requirements, so it is also an accurate indicator of the profit.
+In the case of Bugzilla, they provide an interface to select Priority from a total of five stages, P1 to P5(P1 is the highest).
+The problem with Priority is that there is not much difference in values for each requirement because it is rank-based data.
+And because it's not a required metric, Eclipse has a lot of requirements that don't have priority entered, so it couldn't be used.
+
+\textbf{Number of Comments}: An indicator of how much Discussion has occurred in the requirements.
+We assumed that the requirements would have a high priority if Discussion had occurred in those requirements.
+
+ To find out, we compared the actual Priority to the Number of Comments.
+Figure n shows this as a box plot.
+The higher the priority, the more the comment.
+However, you can see that there are too many outliers and that the data is distributed asymmetrically.
+This is because the number of comments follows a log distribution.
+So we applied the logarithmic function to the number of commands and then we compared it again.
+This is shown in Figure n+1.
+
+As Figure shows, Priority and Member of Comments have a linear relationship.
+Unlike Priority, Number of segments has a constant distribution of values and various values by requirement.
+Number of Comments is better than Priority to apply the actual search-based algorithm.
+
+\textbf{RQ1}.\textit{ Could we estimate PROFIT from Bugzilla without Forward Looking?}
+
+We have concluded that we can speculate on Profit.
+Based on the manager's thinking priority and interest in this requirements, we were able to derive values for the profit between 1 and 5.
+Of course there are limitations.
+Number of comments is not a direct indicator, so exceptions must always be present.
+In addition, if the manager does not enter Priority, such as Eclipse repository, there is a significant lack of confidence in the value.
+If a priority index is entered forcibly, or if a more complex set of indicators such as the number of participants to discussion or number of views is considered, a more accurate profit can be drawn.
+
 \subsection{Cost}
+
+\subsection{Result}
 
@@
 
+\begin{table*}[t]
+\caption{Profit on each limited budget}
+\begin{tabular}{@{}crrrrr@{}}
+\toprule
+\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6}
+\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{AHP} & \multicolumn{1}{c}{ILP} & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} \\ \midrule
+100,000 & 14472.21303& \textbf{14530.92923}& 13787.94014& 13916.62496& 14359.51809\\
+120,000 & 16798.95935& \textbf{16845.48739}& 16269.28033& 16440.60658& 16746.14339\\
+140,000 & 18948.34660& \textbf{18979.35023}& 18553.36746& 18706.04924& 18906.95215\\
+160,000 & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\
+180,000 & 22683.10701& \textbf{22718.92665}& 22332.52554& 22449.04724& 22651.51132\\
+200,000 & 24343.18852& \textbf{24369.86106}& 23894.25792& 24054.60654& 24281.04096\\
+220,000 & 25881.18360& \textbf{25901.23028}& 25425.18545& 25565.45349& 25804.51079\\
+240,000 & 27305.09756& \textbf{27324.51067}& 26790.58789& 26987.08126& 27214.27095\\
+260,000 & 28626.58769& \textbf{28653.54334}& 28161.56720& 28293.21833& 28556.63614\\ \bottomrule
+\end{tabular}
+\label{table:ParetoFront}
+\end{table*}
+
 \subsection{Experiment 1}
@@
 \subsection{Experiment 2}
-\begin{table*}[]
-\caption{Profit on each limited budget}
-\begin{tabular}{@{}crrrrr@{}}
-\toprule
-\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6}
-\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{AHP} & \multicolumn{1}{c}{ILP} & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} \\ \midrule
-100,000 & 14472.21303& \textbf{14530.92923}& 13787.94014& 13916.62496& 14359.51809\\
-120,000 & 16798.95935& \textbf{16845.48739}& 16269.28033& 16440.60658& 16746.14339\\
-140,000 & 18948.34660& \textbf{18979.35023}& 18553.36746& 18706.04924& 18906.95215\\
-160,000 & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\
-180,000 & 22683.10701& \textbf{22718.92665}& 22332.52554& 22449.04724& 22651.51132\\
-200,000 & 24343.18852& \textbf{24369.86106}& 23894.25792& 24054.60654& 24281.04096\\
-220,000 & 25881.18360& \textbf{25901.23028}& 25425.18545& 25565.45349& 25804.51079\\
-240,000 & 27305.09756& \textbf{27324.51067}& 26790.58789& 26987.08126& 27214.27095\\
-260,000 & 28626.58769& \textbf{28653.54334}& 28161.56720& 28293.21833& 28556.63614\\ \bottomrule
-\end{tabular}
-\label{table:ParetoFront}
-\end{table*}
 

### 2018-12-18 PaperBody.tex
Experimental set up edited -> Experiment

@@
 And in Section 5, we're going to apply different search-based algorithms to the datasets that we've created.
-In addition to SA, GA, and NSGA2, we also implemented ILH and AHP directly and applied them to datasets.
+In addition to SA, GA, and NSGA2, we also implemented ILP and AHP directly and applied them to datasets.
 We will apply them to actual datasets and compare the performance of each algorithm in terms of time cost and optimization answers.
@@
 
-We're trying to extract the estimated cost and profit values from the crawled dataset. Our research question can be divided into two main areas.
+We're trying to extract the estimated cost and profit values from the crawled dataset. Our research question about dataset can be divided into two main areas.
 
@@
 
-\section{Experimental Set up}
-In this section, we describe two experiments for comparing algorithms on datasets and analyzing correlation between cost and profit.
+\section{Experiments}
+In this section, we describe what research questions were set and what experiments were performed to answer them.
 We used four datasets(\textit{ECLIPSE, FIREFOX-I, FIREFOX-II} and \textit{FIREFOX-III}) from Bugzilla on experiments which were described in \textbf{section 4}.
 
+\subsection{Research Questions}
+
+The experiments we conducted aim at answering the following research questions:\\
+
+\textbf{RQ3} \textit{Which algorithms are well-suited for our datasets?}
+
+\textbf{RQ4} \textit{Could the different profit strategy affect the performance of algorithm?}
+
 At first experiment(EX1), we applied each algorithm to four datasets in order to compare their performances.
-And we hope to know the effect by different profit strategies through analyzing \textit{FIREFOX-I}, \textit{FIREFOX-II}, and \textit{FIREFOX-III} dataset.
+And we hope to know the effect by different profit strategies through analyzing \textit{FIREFOX-I}, \textit{FIREFOX-II}, and \textit{FIREFOX-III} dataset which are based on FIRFOX dataset but has a different profit strategy.\\
+
+\textbf{RQ5} \textit{What is the correlation between cost and profit?}
 
 At second experiment(EX2), we applied each algorithm to \textit{FIREFOX-III} dataset to analyze the correlation between cost and profit.
-And also, we expected to get the interesting range which have a great change as the limited budget are increased or decreased.
+And also, we expected to get the interesting range which have a great change as the limited budget are increased or decreased.\\
 
+\textbf{RQ6} \textit{Which algorithm and profit strategy are more similar to the real dataset?}
+
+To identify how much our solution are similar to the real world, at third experiment(EX3), we compared the similarity between the real resolved set and the decision vector which is a result of each algorithms.\\
+
+\subsection{Experimental set up}
 All heuristic approaches(SA, GA and NSGA-II) were run for 500,000 function evaluations.

### 2018-12-18 PaperBody.tex
Updates from ShareLaTeX

--- 2018-12-18 PaperBody.tex
@@
 \textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}
-
+\begin{figure*}[h]
+\centering
+  \begin{subfigure}[b]{0.45\linewidth}
+    \includegraphics[width=\linewidth]{images/boxplotraw.png}
+    \caption{Priority-number of comments}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\linewidth}
+    \includegraphics[width=\linewidth]{images/boxplot.png}
+    \caption{Priority-Log(number of comments)}
+  \end{subfigure}
+  \caption{The same cup of coffee. Two times.}
+  \label{fig:priority_comments}
+\end{figure*}
+\begin{figure*}[h]
+\centering
+  \begin{subfigure}[b]{0.9\linewidth}
+    \includegraphics[width=\linewidth]{images/chart_ec.png}
+    \caption{Eclipse}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.9\linewidth}
+    \includegraphics[width=\linewidth]{images/chart_ff.png}
+    \caption{Firefox}
+  \end{subfigure}
+  \caption{Average Time cost at 2016 and 2017 per components}
+  \label{fig:time_cost}
+\end{figure*}
 \subsection{Profit}
@@
  To find out, we compared the actual Priority to the Number of Comments.
-Figure n shows this as a box plot.
+Figure 1.(a) shows this as a box plot.
 The higher the priority, the more the comment.
@@
 So we applied the logarithmic function to the number of commands and then we compared it again.
-This is shown in Figure n+1.
+This is shown in Figure 1.(b)
 
-As Figure shows, Priority and Member of Comments have a linear relationship.
+As Figure 1.(b) shows, Priority and Member of Comments have a linear relationship.
 Unlike Priority, Number of segments has a constant distribution of values and various values by requirement.
@@
 \subsection{Cost}
+
+ Unlike Profit, the Cost was a very difficult task to figure out the actual prediction.
+In fact, it's very difficult for a product manager to calculate the time cost of a particular requirement, and the developers working on the actual task are just guessing how much time they'll take.
+ So we defined the Cost as:
+
+Cost: Average resolution time for the requirements of the same component as the previous year
+
+Bugzilla's repositories are divided into each component.
+We assumed that the average time it takes to fix the bug for each component would be a constant in next year.
+Therefore, We concluded that the average bug modification time for each component in 2017 would not be much different from 2016.
+So the Cost of each requirement was used as a prediction index for the average Cost of that component in 2016.
 

### 2018-12-18 PaperBody.tex
add result at section4

@@
     \midrule
-    Reported in 2017& 1 & 1 \\
-    Resolved in 2018 & 1&1 \\
+    Reported in 2017& 2053 & 5593 \\
+    Resolved in 2018 & 817 & 2938 \\
     \bottomrule
@@
   \end{subfigure}
-  \caption{The same cup of coffee. Two times.}
+  \caption{The relation ship between Priority and Number of Comments}
   \label{fig:priority_comments}
@@
 
-Cost: Average resolution time for the requirements of the same component as the previous year
+\textbf{Cost}: \textit{Average resolution time for the requirements of the same component as the previous year}
 
@@
 
+ To illustrate this, we compared the average time cost in 2016 to the average time cost in 2017. Figure 2 describes this.
+
+As Figure 2.(a) shows, the first, the result in Eclipse repository is quite accurate.
+The average bug resolution time was similar than we expected.
+Some exceptions have been found to exist, but more than 60 percent of the components actually match.
+
+But for Figure 2.(b) the result in Firefox repository, we can also see that the order of each component, including absolute time-consuming values, is not quite correct.
+In Firefox, it was updated almost 200 times a year.
+Therefore, in 2016 and 2017, the code was not maintained the same, so it make that the actual cost are not constant among the years.
+
+\textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}
+
+We have concluded that it is possible to use the past Cost only for projects where updates are infrequent, i.e.
+projects with some constant structure.
+This estimate process has many limitations to be used in real industry.
+It's a very change-sensitive indicator, and it has the potential to be wrong at any time.
+However, in order to estimate this more accurately, it would be the only way for the developer or project manager to specify the actual estimated time cost.
+In the absence of such direct data, our estimates will be meaningful.
+
 \subsection{Result}
-
+In conclusion, we were able to create 4 data sets.
 \begin{table} [H]
@@
     \toprule
-    &ECLIPSE&FIREFOX-I&FIREFOX-II&FIREFOX-III\\
+    Repository&Profit definition&True Cost&True Profit\\
+    % &ECLIPSE&FIREFOX-I&FIREFOX-II&FIREFOX-III\\
     \midrule
-    Cost& 50699.70& 262945.50& 262945.50& 262945.50 \\
-    Profit& 3489.64& 13025.88& 12210& 26332.88 \\
+    ECLIPSE-I&Log(comments)&50699.70& 3489.64 \\
+    FIREFOX-I&Log(comments)& 262945.50& 13025.8 \\
+    FIREFOX-II&Priority& 262945.50& 12210 \\
+    FIREFOX-III&Priority+Log(comments)& 262945.50& 26332.88 \\
     \bottomrule
@@
 \end{table}
+
+In Firefox, the profit was able to use both Priority and Number of Comments, creating a total of three data sets, including each case and the sum of the two indicators.
+The table also shows the true value of cost & profit that was resolved in 2018.
+We're going to use this dataset to compare the results of the actual search-based algorithms in the next section.
 

### 2018-12-18 PaperBody.tex
Updates from ShareLaTeX

--- 2018-12-18 PaperBody.tex
@@
 \textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}
-\begin{figure*}[h]
-\centering
-  \begin{subfigure}[b]{0.45\linewidth}
-    \includegraphics[width=\linewidth]{images/boxplotraw.png}
-    \caption{Priority-number of comments}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.45\linewidth}
-    \includegraphics[width=\linewidth]{images/boxplot.png}
-    \caption{Priority-Log(number of comments)}
-  \end{subfigure}
-  \caption{The same cup of coffee. Two times.}
-  \label{fig:priority_comments}
-\end{figure*}
-\begin{figure*}[h]
-\centering
-  \begin{subfigure}[b]{0.9\linewidth}
-    \includegraphics[width=\linewidth]{images/chart_ec.png}
-    \caption{Eclipse}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.9\linewidth}
-    \includegraphics[width=\linewidth]{images/chart_ff.png}
-    \caption{Firefox}
-  \end{subfigure}
-  \caption{Average Time cost at 2016 and 2017 per components}
-  \label{fig:time_cost}
-\end{figure*}
+
 \subsection{Profit}
@@
  To find out, we compared the actual Priority to the Number of Comments.
-Figure 1.(a) shows this as a box plot.
+Figure n shows this as a box plot.
 The higher the priority, the more the comment.
@@
 So we applied the logarithmic function to the number of commands and then we compared it again.
-This is shown in Figure 1.(b)
+This is shown in Figure n+1.
 
-As Figure 1.(b) shows, Priority and Member of Comments have a linear relationship.
+As Figure shows, Priority and Member of Comments have a linear relationship.
 Unlike Priority, Number of segments has a constant distribution of values and various values by requirement.
@@
 \subsection{Cost}
-
- Unlike Profit, the Cost was a very difficult task to figure out the actual prediction.
-In fact, it's very difficult for a product manager to calculate the time cost of a particular requirement, and the developers working on the actual task are just guessing how much time they'll take.
- So we defined the Cost as:
-
-Cost: Average resolution time for the requirements of the same component as the previous year
-
-Bugzilla's repositories are divided into each component.
-We assumed that the average time it takes to fix the bug for each component would be a constant in next year.
-Therefore, We concluded that the average bug modification time for each component in 2017 would not be much different from 2016.
-So the Cost of each requirement was used as a prediction index for the average Cost of that component in 2016.
 
@@
 
-\caption{Profit Comparison for each dataset}
+\caption{EX1 - Profit Comparison for each dataset}
 \label{fig:DatasetProfit}
@@
 
-At second experiment(EX2), we applied each algorithm to \textit{FIREFOX-III} dataset to analyze the correlation between cost and profit.
-And also, we expected to get the interesting range which have a great change as the limited budget are increased or decreased.\\
+At second experiment(EX2), we applied each algorithm to \textit{FIREFOX-III} dataset to see the correlation between cost and profit under the real estimated cost.
+And also, we expected to get the interesting range which have a great change as the limited budget are increased or decreased.
+For example, let's assume $R = {r_1, r_2, \ldots, r_5}$, $Cost = {10, 9, 8, 2, 1}$ and $Profit = {10, 9, 8, 2, 1}$.
+Then, if we see the maximum profit while decreasing the limited budget, we can verify that there is a peculiar point which have a great change of profit when the limited budget is 7.
+So, if possible, we wanted to verify a peculiar part on EX2.
+\\
 
@@
 \section{Result and Analysis}
+All results of heuristic algorithms are averaged.\\
+
+\textbf{RQ3}\textit{Which algorithms are well-suited for our datasets?}
+
+At EX1, we applied two deterministic and three heuristic algorithms to four datasets and compared the averaged maximum profit to each other.
+Figure \ref{fig:DatasetProfit} shows the results of EX1.
+Each graph expresses the profit of five algorithms under the limited budget(= the estimated cost).
+
+In these results, the profit of each algorithm were bigger than the real profit in Table \ref{table:Dataset}.
+And, in every case, the ILP has the biggest profit.
+However, the order of other algorithms are slightly changed for dataset.
+
+The SA has the smallest profit in most cases, except Figure \ref{fig:DatasetProfit}-(c).
+Although the SA started from a greedy solution, there is little difference between the result and a greedy solution.
+The profit of GA is bigger than SA and smaller than NSGA-II in every cases.
+So, the profit is high in order of NSGA-II, GA, then SA.
+The AHP has good performances for some cases.
+However, it has the lowest profit in \ref{fig:DatasetProfit}-(c).
+
+The run time is also critical point to evaluate the performance.
+The run time of two deterministic algorithms takes just a few seconds.
+However, the run time of three heuristic algorithms takes more than 10 minutes.
+Although we consider that ILP used ILP solver, the run time of deterministic algorithms were much faster than heuristic algorithms.
+
+Therefore, we can conclude that the ILP is well-suited for our datasets and also it is much faster than other heuristic algorithms.\\
+
+\textbf{RQ4} \textit{Could the different profit strategy affect the performance of algorithm?}
+
+To see the effect of different profit strategy, let's see the figure \ref{fig:DatasetProfit}-(b), (c), and (d) which are based on FIREFOX dataset but each of them has a different profit strategy.
+In the figure \ref{fig:DatasetProfit}-(b) and (d), GA has much bigger profit than SA and AHP has good performances enough to exceed NSGA-II.
+However, In the figure \ref{fig:DatasetProfit}-(c), GA has just little improvement from a greedy solution and AHP has the lowest profit among all algorithms.
+Therefore, we identified that the different profit strategy can affect the performance of algorithms.\\
+
+\textbf{RQ5} \textit{What is the correlation between cost and profit?}
+
+At EX2, we got the profits while changing the cost constraint.
+The result is expressed in Table \ref{table:ParetoFront}.
+In the results, profits of each algorithms are all increasing almost similarly and the order of profits(ILP, AHP.
+NSGA-II, GA, then SA) are same in every case.
+And also, we observed that the change of profits become smaller as the limited budget increases.
+
+One of the reasons to perform EX2 was that we wondered if there is a peculiar part in cost-profit graph. However, we cannot observe prominently peculiar part on EX2.\\
+
+\textbf{RQ6} \textit{Which algorithm and profit strategy are more similar to the real dataset?}
 
@@
 \begin{table*}[t]
-\caption{Profit on each limited budget}
+\caption{EX2 - Profit on each limited budget}
 \begin{tabular}{@{}crrrrr@{}}
@@
 \end{table*}
-
-\subsection{Experiment 1}
-At EX1, we applied two deterministic and three heuristic algorithms to four datasets and compared the averaged maximum profit to each other.
-Figure \ref{fig:DatasetProfit} shows the results of EX1.
-Each graph expresses the profit of five algorithms under the limited budget(= the estimated cost).
-
-In these results, the profit of each algorithm were bigger than the real profit in Table \ref{table:Dataset}.
-And, in every case, the ILP has the biggest profit.
-However, the order of other algorithms are slightly changed for dataset.
-
-The SA has the smallest profit in most cases, except Figure \ref{fig:DatasetProfit}-(c).
-Although the SA started from a greedy solution, there is little difference between the result and a greedy solution.
-The profit of GA is bigger than SA and smaller than NSGA-II in every cases.
-So, the profit is high in order of NSGA-II, GA, then SA.
-The AHP has good performances for some cases.
-However, it has the lowest profit in \ref{fig:DatasetProfit}-(c).
-Therefore, we can conclude that the strategy about evaluating profit can be affect the results.
-
-The run time of two deterministic algorithms were much faster than heuristic algorithms.
-Therefore, we can conclude that the ILP is well-suited for our datasets and also it is much faster than other heuristic algorithms.
-
-\subsection{Experiment 2}
-
-At EX2, we got the profits while changing the cost constraint.
-The result is expressed in Table \ref{table:ParetoFront}.
-In the results, profits of each algorithms are all increasing almost similarly and the order of profits(ILP, AHP.
-NSGA-II, GA, then SA) are same in every case.
-And also, we observed that the change of profits become smaller as the limited budget increases.
-
-One of the reasons to perform EX2 was that we wondered if there is a peculiar part in cost-profit graph. However, we cannot observe prominently peculiar part in the dataset.
 

### 2018-12-18 PaperBody.tex
Updates from ShareLaTeX
add heatmap

@@
 \textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}
-\begin{figure*}[h]
+
+\begin{figure*}
 \centering
@@
 \subsection{Result}
+
 In conclusion, we were able to create 4 data sets.
+In Firefox, the profit was able to use both Priority and Number of Comments, creating a total of three data sets, including each case and the sum of the two indicators.
+The table also shows the true value of cost and profit that was resolved in 2018.
+We're going to use this dataset to compare the results of the actual search-based algorithms in the next section.
+
 \begin{table} [H]
@@
 \end{table}
-
-In Firefox, the profit was able to use both Priority and Number of Comments, creating a total of three data sets, including each case and the sum of the two indicators.
-The table also shows the true value of cost & profit that was resolved in 2018.
-We're going to use this dataset to compare the results of the actual search-based algorithms in the next section.
 
@@
 The \textit{make-new-pop} function consist of tournament selection, cross-over, and mutation operator which are used to create a child population.
+And,
 
@@
 
-To identify how much our solution are similar to the real world, at third experiment(EX3), we compared the similarity between the real resolved set and the decision vector which is a result of each algorithms.\\
+To identify how much our solution are similar to the real world, at third experiment(EX3), we compared the similarity between the real resolved set and the decision vector which is a result of each algorithms.
 

### 2018-12-18 PaperBody.tex
conclusion
Conclusion
Updates from ShareLaTeX

@@
 
-https://github.com/shkevinlee/CS454
+https://github.com/shkevinlee/CS454 \\ and the brief test implementation is described in \textbf{Test.py} in there.
 
@@
 
-%At first experiment, we applied five algorithms to four datasets and compared the maximum profit each other.
-In \textbf{Table \ref{table:DatasetProfit}}, upper two rows are estimated cost sum and real profit sum of each datasets.
-Below these rows, there are averaged profits for each algorithms on four datasets.
-At the result, every profits for algorithms are bigger than real profit sum.
-Also, consumed time to return maximum profit was exceedingly short in ILP and AHP, rather than SA, GA, and NSGA-II.
-
-%\textbf{Figure \ref{fig:DatasetProfit}} is the graphs of \textbf{table 1}.
-Each graph %expresses the averaged profit of five algorithms.
-At the result, the profit of ILP is %the biggest, and the profit of NSGA-II and AHP is bigger than SA and GA in most case.
-%Except ILP and AHP, maximum profit is high in order of NSGA-II, GA, then SA.
-
-%At experiment 2, we got the profits while changing the cost constraint.
-The result is expressed in \textbf{Figure \ref{fig:paretofronts}}.
-\textbf{Figure \ref{fig:paretofronts}} expresses maximum profits on each cost, and \textbf{Figure 3} is integrating graph of \textbf{Figure 2} because of comparing the difference for four algorithms.
-
-%The result is that they are all increasing almost similarly.
-One of the reasons to perform this experiment was that we wondered if there is a peculiar part in cost-profit graph.(if there is exceeding increase in profit) And at the result, there is no prominently peculiar part, and all the results are increasing normally.
-
 \begin{table*}[t]
@@
 
+\begin{figure*}[h]
+\centering
+  \begin{subfigure}[b]{0.95\linewidth}
+    \includegraphics[width=\linewidth]{images/heatmap_ec.png}
+  \end{subfigure}
+  \caption{EX3-Requirements Heatmap in Eclipse Repositories(white = selected, Black = unselected)}
+  \label{fig:EclipseHeatmap}
+\end{figure*}
+
 \section{Conclusion}
@@
 And deterministic algorithms that AHP and ILP are very fast than heuristic algorithms.
+And Ex1 can answer RQ3 and RQ4.
 Ex2.
@@
 As we mentioned, we found that limits of the Cost and the Profit had a linear relationship, regardless of algorithm.
+but it doesn't seem have much meaning.
+In RQ6.
+The result of algorithms were similar to those actual selection.
 These results show that tere are no major problems with applying NRP argorithms to our dataset.

### 2018-12-18 PaperBody.tex

@@
 
+\begin{table*}[t]
+\caption{EX3 - Recal of each algorithms on four datasets}
+\begin{tabular}{@{}crrrrr@{}}
+\toprule
+\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6}
+\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} & \multicolumn{1}{c}{AHP} & \multicolumn{1}{c}{ILP} \\ \midrule
+ECLIPSE & 0.77300 & 0.81435 & 0.82025 & 0.82700 & 0.82363\\
+FIREFOX-I & 0.82973 & 0.00000 & 0.85876 & 0.86721 & 0.87302\\
+FIREFOX-II & 0.56917 & 0.00000 & 0.60507 & 0.61536 & 0.79725\\
+FIREFOX-III & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\\bottomrule
+\end{tabular}
+\label{table:Recall}
+\end{table*}
+
 \begin{figure*}[h]

### 2018-12-18 PaperBody.tex
add heatmap on progress

@@
   \end{subfigure}
-  \caption{EX3-Requirements Heatmap in Eclipse Repositories(white = selected, Black = unselected)}
+  \caption{EX3-Requirements Heatmap in ECLIPSE-I(white = selected, Black = unselected)}
   \label{fig:EclipseHeatmap}
 \end{figure*}
-
+\begin{figure*}[h]
+\centering
+  \begin{subfigure}[b]{0.95\linewidth}
+    \includegraphics[width=\linewidth]{images/heatmap_ff1.png}
+  \end{subfigure}
+  \caption{EX3-Requirements Heatmap in FIREFOX-I(white = selected, Black = unselected)}
+  \label{fig:EclipseHeatmap}
+\end{figure*}
+\begin{figure*}[h]
+\centering
+  \begin{subfigure}[b]{0.95\linewidth}
+    \includegraphics[width=\linewidth]{images/heatmap_ff3.png}
+  \end{subfigure}
+  \caption{EX3-Requirements Heatmap in FIREFOX-III(white = selected, Black = unselected)}
+  \label{fig:EclipseHeatmap}
+\end{figure*}
 \section{Conclusion}

### 2018-12-18 PaperBody.tex
add all heatmap
Updates from ShareLaTeX

--- 2018-12-18 PaperBody.tex
@@
 
+Table \ref{table:Recall} and figure \ref{fig:EclipseHeatmap} show the results of the EX3.
+In table \ref{table:Recall}, we presented the recall of each algorithms.
+The recall is the ratio between the number of $1$s in the decision vector $\textbf{x}$ and the number of resolved requirements in the real dataset.
+In ECLIPSE, FIREFOX-I, and FIREFOX-III, we can verify that each algorithms has a high recall values above 0.75 and the recall value increases as higher maximum profit was got in EX1.
+It can be easily confirmed on figure \ref{fig:EclipseHeatmap}.
+Therefore, we can concludet that the profit strategy of ECLIPSE, FIREFOX-I and FIREFOX-III are similar to the real world dataset.
+
+However, in FIREFOX-II, all algorithms had lower recall values than other datasets. But we can see that AHP has much higher recall values than other algorithms.
+
+In the table, we can verify that it has a high recall value as higher maximum profit in EX1, except FIREFOX-II.
+
 \begin{table*}[t]
@@
 \label{table:ParetoFront}
+\end{table*}
+
+\begin{table*}[t]
+\caption{EX3 - Recall of each algorithms on four datasets}
+\begin{tabular}{@{}crrrrr@{}}
+\toprule
+\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6}
+\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} & \multicolumn{1}{c}{ILP} & \multicolumn{1}{c}{AHP} \\ \midrule
+ECLIPSE & 0.77300 & 0.81435 & 0.82025 & \textbf{0.82700} & 0.82363\\
+FIREFOX-I & 0.82973 & 0.00000 & 0.85876 & 0.86721 & \textbf{0.87302}\\
+FIREFOX-II & 0.56917 & 0.00000 & 0.60507 & 0.61536 & \textbf{0.79725}\\
+FIREFOX-III & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\\bottomrule
+\end{tabular}
+\label{table:Recall}
 \end{table*}

### 2018-12-18 PaperBody.tex

@@
   \end{subfigure}
-  \caption{EX3-Requirements Heatmap in Eclipse Repositories(white = selected, Black = unselected)}
+  \caption{EX3-Requirements Heatmap in ECLIPSE-I(white = selected, Black = unselected)}
   \label{fig:EclipseHeatmap}
 \end{figure*}
-
+\begin{figure*}[h]
+\centering
+  \begin{subfigure}[b]{0.95\linewidth}
+    \includegraphics[width=\linewidth]{images/heatmap_ff1.png}
+  \end{subfigure}
+  \caption{EX3-Requirements Heatmap in FIREFOX-I(white = selected, Black = unselected)}
+  \label{fig:EclipseHeatmap}
+\end{figure*}
+\begin{figure*}[h]
+\centering
+  \begin{subfigure}[b]{0.95\linewidth}
+    \includegraphics[width=\linewidth]{images/heatmap_ff2.png}
+  \end{subfigure}
+  \caption{EX3-Requirements Heatmap in FIREFOX-II(white = selected, Black = unselected)}
+  \label{fig:EclipseHeatmap}
+\end{figure*}
+\begin{figure*}[h]
+\centering
+  \begin{subfigure}[b]{0.95\linewidth}
+    \includegraphics[width=\linewidth]{images/heatmap_ff3.png}
+  \end{subfigure}
+  \caption{EX3-Requirements Heatmap in FIREFOX-III(white = selected, Black = unselected)}
+  \label{fig:EclipseHeatmap}
+\end{figure*}
 \section{Conclusion}

### 2018-12-18 PaperBody.tex
Table added

@@
 ECLIPSE & 0.77300 & 0.81435 & 0.82025 & \textbf{0.82700} & 0.82363\\
-FIREFOX-I & 0.82973 & 0.00000 & 0.85876 & 0.86721 & \textbf{0.87302}\\
-FIREFOX-II & 0.56917 & 0.00000 & 0.60507 & 0.61536 & \textbf{0.79725}\\
-FIREFOX-III & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\\bottomrule
+FIREFOX-I & 0.82973 & 0.83395 & 0.85876 & 0.86721 & \textbf{0.87302}\\
+FIREFOX-II & 0.56917 & 0.57154 & 0.60507 & 0.61536 & \textbf{0.79725}\\
+FIREFOX-III & 0.68268 & 0.70486 & 0.74155 & 0.76637 & 0.78300\\\bottomrule
 \end{tabular}

### 2018-12-18 PaperBody.tex
final
Real Final

@@
 One of the reasons to perform EX2 was that we wondered if there is a peculiar part in cost-profit graph. However, we cannot observe prominently peculiar part on EX2.\\
-
-\textbf{RQ6} \textit{Which algorithm and profit strategy are more similar to the real dataset?}
-
-Table \ref{table:Recall} and figure \ref{fig:EclipseHeatmap} show the results of the EX3.
-In table \ref{table:Recall}, we presented the recall of each algorithms.
-The recall is the ratio between the number of $1$s in the decision vector $\textbf{x}$ and the number of resolved requirements in the real dataset.
-In ECLIPSE, FIREFOX-I, and FIREFOX-III, we can verify that each algorithms has a high recall values above 0.75 and the recall value increases as higher maximum profit was got in EX1.
-It can be easily confirmed on figure \ref{fig:EclipseHeatmap}.
-Therefore, we can concludet that the profit strategy of ECLIPSE, FIREFOX-I and FIREFOX-III are similar to the real world dataset.
-
-However, in FIREFOX-II, all algorithms had lower recall values than other datasets. But we can see that AHP has much higher recall values than other algorithms.
-
-In the table, we can verify that it has a high recall value as higher maximum profit in EX1, except FIREFOX-II.
-
 \begin{table*}[t]
@@
 \end{table*}
-
 \begin{table*}[t]
@@
 FIREFOX-II & 0.56917 & 0.57154 & 0.60507 & 0.61536 & \textbf{0.79725}\\
-FIREFOX-III & 0.68268 & 0.70486 & 0.74155 & 0.76637 & 0.78300\\\bottomrule
+FIREFOX-III & 0.68268 & 0.70486 & 0.74155 & 0.76637 & \textbf{0.78300}\\\bottomrule
 \end{tabular}
@@
 \end{table*}
+
+\textbf{RQ6} \textit{Which algorithm and profit strategy are more similar to the real dataset?}
+
+Table \ref{table:Recall}, figure \ref{fig:EclipseHeatmap}, figure \ref{fig:FirefoxIHeatmap}, figure \ref{fig:FirefoxIIHeatmap} and figure \ref{fig:FirefoxIIIHeatmap} show the results of the EX3.
+In table \ref{table:Recall}, we presented the recall of each algorithms.
+The recall is the ratio between the number of $1$s which is also resolved in dataset in the decision vector $\textbf{x}$ and the number of resolved requirements in the real dataset.
+In ECLIPSE and FIREFOX-I, we can verify that each algorithms has a high recall values above 0.75 and the recall value increases as higher maximum profit was got in EX1.
+It can be easily confirmed on figure \ref{fig:EclipseHeatmap} and \ref{fig:FirefoxIHeatmap}.
+Therefore, we can conclude that the profit strategy of ECLIPSE and FIREFOX-I which use the log of comments are similar to the real world dataset.
+
+However, in FIREFOX-II, all algorithms had lower recall values than other datasets.
+But we can see that AHP has much higher recall values than other algorithms.
+It is not matched result to EX1.
+In the figure \ref{fig:DatasetProfit}-(c) which is the result of EX1 on FIREFOX-II, AHP had the lowest profit among the algorithms.
+Therefore, we can conclude that the profit strategy of FIREFOX-II is not matched to the real world.
+
+The result of FIREFOX-III was between FIREFOX-I and FIREFOX-II because its profit strategy is the mixed version of them.
+
+In most cases, AHP has the best recall values among the algorithms.
+But FIREFOX-II and FIREFOX-III are concluded that they are not matched to real dataset, and in the ECILPSE, ILP has a higher recall value than AHP.
+Therefore, we cannot conclude which algorithms are more similar to the real dataset.
 
@@
   \caption{EX3-Requirements Heatmap in FIREFOX-I(white = selected, Black = unselected)}
-  \label{fig:EclipseHeatmap}
+  \label{fig:FirefoxIHeatmap}
 \end{figure*}
@@
   \caption{EX3-Requirements Heatmap in FIREFOX-II(white = selected, Black = unselected)}
-  \label{fig:EclipseHeatmap}
+  \label{fig:FirefoxIIHeatmap}
 \end{figure*}
@@
   \caption{EX3-Requirements Heatmap in FIREFOX-III(white = selected, Black = unselected)}
-  \label{fig:EclipseHeatmap}
+  \label{fig:FirefoxIIIHeatmap}
 \end{figure*}
@@
 The result of algorithms were similar to those actual selection.
-These results show that tere are no major problems with applying NRP argorithms to our dataset.
+These results show that there are no major problems with applying NRP argorithms to our dataset.
 Therefore, the dataset was well set to solve the NRP.

### 2018-12-18 PaperBody.tex
Real Final~!!

@@
 was profit comparison.
-Exept for dataset with priority, the ILP has the highest result.
+Except for dataset with priority, the ILP has the highest result.
 And deterministic algorithms that AHP and ILP are very fast than heuristic algorithms.
@@
 In RQ6.
-The result of algorithms were similar to those actual selection.
-These results show that there are no major problems with applying NRP argorithms to our dataset.
+The result of algorithms were similar to those actual selection except FIREFOX-II.
+These results show that there are no major problems with applying NRP algorithms to our dataset.
 Therefore, the dataset was well set to solve the NRP.
